---
title: "3_examine_classification_outputs"
author: "Bria Long"
date: "11/20/2018"
output: 
  html_document:
    toc: true # make table of contents
    toc_depth: 3
    theme: united
    highlight: tango 
---

```{r setup, include=FALSE}
library(tidyverse)
library(readr)
library(assertthat)
library(knitr)
library(ggplot2)
library(ggthemes)
library(lme4)
```

## Read in and clean up datafiles
### Read in classification outputs (from get_classifications.py)
```{r}
meta <- read.csv('classification-outputs/museumstation_subset_classification.csv') %>%
  as.tibble() %>%
  mutate(session_id = paste('cdm_',session_ids,sep="")) %>%
  mutate(age_numeric = ages) %>%
  mutate(age = paste('age',ages,sep="")) %>%
  mutate(category = target_classes) %>%
  select(-X)
```

### Merge with mongodb database outputs (stroke count, duration, etc.)
Now should be able to look at target label probabilties for each image as a function of all of these other factors
```{r}
mongodb_meta <- read.csv('mongodb-output/MuseumStation_AllDescriptives_20780_images_final_cdm_run_v3.csv') %>%
  as.tibble() %>%
  left_join(meta) %>% # should join on session_id, category, age -- combination of which is unique identifier for an image
  filter(!is.na(target_label_prob)) # if intermediate file, only look where we have data

# main variable with merged data
d<- mongodb_meta
```
## Basic plots 
### age x log_probability of target class
```{r}
ggplot(d, aes(age_numeric,log(target_label_prob), color=image_scores)) +
  geom_point(alpha=.5) +
  theme_few() + 
  geom_smooth() +
  facet_wrap(~category) +
  labs(x='Age', y='Log probability', color="correctly classified?")
```

### age x classification accuracy 
```{r}
ggplot(d, aes(age_numeric,image_scores)) +
  theme_few() + 
  geom_jitter(alpha=.2, height=0, width=.2) +
  geom_smooth() + 
  facet_wrap(~category)
```

### Num strokes x target_label_prob
```{r}
ggplot(d, aes(num_strokes,log(target_label_prob), color=image_scores)) +
  geom_point(alpha=.5) +
  theme_few() + 
  geom_smooth(method='lm') +
  facet_wrap(~category)
```

### Mean intensity x target_label_prob
```{r}
ggplot(d, aes(mean_intensity,log(target_label_prob), color=image_scores)) +
  geom_point(alpha=.5) +
  theme_few() + 
  geom_smooth(method='lm') +
  facet_wrap(~category)
```

### Draw duration x target_label_prob
```{r}
ggplot(d, aes(draw_duration_old,log(target_label_prob), color=image_scores, names = "recognized or not")) +
  geom_point(alpha=.5) +
  theme_few() + 
  geom_smooth(method='lm') +
  facet_wrap(~category) +
  labs(x='Time spent drawing', y='Log probability', color="correctly classified?")
```

## Inferential stats
### Generalized linear mixed model with all covariates 
```{r}
# mod_covariates <- glmer(image_scores ~ scale(age_numeric) + 
#                           scale(draw_duration_old) + 
#                           scale(mean_intensity) + 
#                           scale(num_strokes) +
#                         (1|session_id) + 
#                         (1|category), 
#       data = d,  
#       family = "binomial")
# modelOut=summary(mod_covariates)
# kable(summary(mod_covariates)$coef, digits = 3)

```

### Generalized linear mixed model with all covariates *and their interactions*
``` {r}
# mod_covariates_age <- glmer(image_scores ~ (scale(age_numeric) + 
#                           scale(draw_duration_old) + 
#                           scale(num_strokes))^2 +
#                         (1|session_id), 
#       data = d,  
#       family = "binomial")
# kable(summary(mod_covariates_age)$coef, digits = 3)
```
