---
title: "AnimalGame-Descriptives-Check"
author: ""
date: "2/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)
library(ggplot2)
library(assertthat)
library(langcog)
library(viridis)
library(ggthemes)
```

## Import descriptives csv
```{r cars}
d <- read.csv("recognition_data/biganimalgame_out_jan19.csv") %>%
  as.tibble() 
```

### Look at counts by producer_age and category
```{r cat-by-condition-by-age}

d %>%
  group_by(producer_age,intended_category) %>%
  summarize(num_drawings = n()) %>%
  kable()

```

### Look at counts by individual sketch; should be low at first and randomly distributed
```{r}
guess_by_sketch <- d %>%
  filter(producer_age != 'photo') %>% ## exclude catch trials
  group_by(sketch_path, intended_category, producer_age) %>%
  summarize(num_guesses = n()) 
  # kable()
```

We have an average of `r mean(guess_by_sketch$num_guesses)` trials per individual sketch.

### Preprocess dataset
```{r}
# make similar levels
d$intended_category <- factor(d$intended_category, levels=levels(d$clicked_category))

# compute accurcy
d <- d %>%
  mutate(correct_or_not = (clicked_category == intended_category))  

d$recognizer_age <- factor(d$recognizer_age, levels = c('age2','age3','age4','age5','age6','age7','age8','age9','age10','adult'))
```

## Filter non-compliant subjects
```{r}
# get list of non-compliant subs
bad_subs <- d %>%
  group_by(sessionId) %>%
  filter(producer_age == "photo") %>%
  summarize(avg_photo_correct = mean(correct_or_not), count_trials = n()) %>%
  filter(avg_photo_correct < .5) 

# filter bad subs
d <- d %>%
  filter(!sessionId %in% bad_subs$sessionId) 

```

We excluded `r length(bad_subs$sessionId)` subjects for having 'photo' accuracies of less than 50% correct; these subjects completed an average of `r mean(bad_subs$count_trials)` trials.

## How many subjects do we have?
```{r}
(count_data <- d %>%
  group_by(recognizer_age) %>%
  summarize(count_subs = length(unique(sessionId)), total_trials = n()))

```

## Compile averages to look at average correct
```{r plot-counts}
# summarize avg correct by producer age  
by_producer <- d %>%
  filter(recognizer_age!= 'adult') %>%
  group_by(producer_age) %>%
  multi_boot_standard(col = 'correct_or_not')

by_recognizer <- d %>%
  group_by(recognizer_age) %>%
  filter(producer_age != 'photo') %>%
  multi_boot_standard(col = 'correct_or_not')

by_recognizer_photo <- d %>%
  group_by(recognizer_age) %>%
  filter(producer_age == 'photo') %>%
  multi_boot_standard(col = 'correct_or_not') 


both <- d %>%
  group_by(recognizer_age,producer_age) %>%
  multi_boot_standard(col = 'correct_or_not') 
```

### Compile averages by RT
```{r}
# summarize avg correct by producer age  
by_producer_rt <- d %>%
  filter(recognizer_age!= 'adult') %>%
  group_by(producer_age) %>%
  filter(correct_or_not == TRUE) %>%
  filter(RT > 300 & RT < 20000) %>%
  multi_boot_standard(col = 'RT')

by_recognizer_rt <- d %>%
  group_by(recognizer_age) %>%
  filter(correct_or_not == TRUE) %>%
  filter(producer_age != 'photo') %>%
 filter(RT > 300 & RT < 20000) %>%
  multi_boot_standard(col = 'RT')

by_recognizer_photo_rt <- d %>%
  group_by(recognizer_age) %>%
  filter(producer_age == 'photo') %>%
  filter(correct_or_not == TRUE) %>%
  filter(RT > 300 & RT < 20000) %>%
  multi_boot_standard(col = 'RT') 

both_rt <- d %>%
  group_by(recognizer_age,producer_age) %>%
  filter(correct_or_not == TRUE) %>%
  filter(RT > 300 & RT < 10000) %>%
  multi_boot_standard(col = 'RT') 

```

### Plot at how each group is doing on the photo catch trials (this excludes 'bad' subs)
```{r}
by_recognizer$recognizer_age <- factor(by_recognizer$recognizer_age, levels = c('age2','age3','age4','age5','age6','age7','age8','age9','age10','adult'))

ggplot(by_recognizer_photo,aes(x=recognizer_age, y=mean, col = recognizer_age)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  scale_color_viridis(discrete = "TRUE") + 
  ylab('Proportion recognized')
```

```{r}
by_recognizer_photo$recognizer_age <- factor(by_recognizer_photo$recognizer_age, levels = c('age2','age3','age4','age5','age6','age7','age8','age9','age10','adult'))

ggplot(by_recognizer_photo,aes(x=recognizer_age, y=mean, col = recognizer_age)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  scale_color_viridis(discrete = "TRUE") + 
  ylab('Proportion recognized - PHOTO')
```

### By producer age, collapsing across recognizer age
```{r}
ggplot(by_producer,aes(x=producer_age, y=mean, col = producer_age)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  scale_color_viridis(discrete = "TRUE") + 
  ylab('Proportion recognized')
```

## Now looking at producer x recognizer age
```{r}
both$recognizer_age <- factor(both$recognizer_age, levels = c('age2','age3','age4','age5','age6','age7','age8','age9','age10','adult'))

ggplot(both,aes(x=producer_age, y=mean, col=recognizer_age)) +
  theme_few() + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ylab('average correct') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), aspect.ratio = 1) +
  facet_grid(~recognizer_age) 
```

### Switch recognizer/producer age to re-visualize data
```{r}
both_plot <- both %>%
  group_by(recognizer_age)

ggplot(both_plot,aes(x=recognizer_age, y=mean, col=producer_age)) +
  theme_few() + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ylab('average correct') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), aspect.ratio = 1) +
  facet_grid(~producer_age) +
  scale_color_viridis(discrete=TRUE) +
  geom_smooth()

```

### Check out RTs
```{r}
both_rt$recognizer_age <- factor(both_rt$recognizer_age, levels = c('age2','age3','age4','age5','age6','age7','age8','age9','age10','adult'))

ggplot(both_rt,aes(x=producer_age, y=mean, col=recognizer_age)) +
  # geom_point() + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab('average RT') + 
  facet_grid(~recognizer_age) 
```


```{r}
library(lme4)
 model_lmer <- glmer(correct_or_not ~ producer_age*recognizer_age + (1 | intended_category),  data = d, family="binomial", optimizer="bobqa")


```