---
title: "Examine LOO classification outputs (data subset)"
author: "Bria Long"
date: "started 11/20/2018"
output: 
  html_document:
    toc: true # make table of contents
    toc_depth: 3
    theme: united
    highlight: tango 
---

```{r setup, include=FALSE}
library(tidyverse)
library(readr)
library(assertthat)
library(knitr)
library(ggplot2)
library(reshape2)
library(ggthemes)
library(lme4)
library(stringr)
library(magick) # for making montages
library(langcog)
library(viridis)
library(egg)
```

## Read in and clean up datafiles
### Read in classification outputs (from get_classifications.py)


```{r}
meta <- read.csv('classification-outputs/museumstation_subset_classification.csv') %>%
  as.tibble() %>%
  mutate(session_id = paste('cdm_',session_ids,sep="")) %>%
  mutate(age_numeric = ages) %>%
  mutate(age = paste('age',ages,sep="")) %>%
  mutate(category = target_classes) %>% 
  mutate(category_short = str_split_fixed(category," ",2)[,2]) %>%
  mutate(image_name = paste(category,'_sketch_', age,'_', session_id,'.png',sep="")) %>%
  select(-X) 
```


```{r}
makeConfusions<- function(meta,target_age){
  confusions <- meta %>%
  group_by(category_short) %>%
  filter(age_numeric == target_age ) %>%
  summarize(bike = mean(a.bike.prob), bird = mean(a.bird.prob), boat = mean(a.boat.prob), bowl = mean(a.bowl.prob), car = mean(a.car.prob), chair = mean(a.chair.prob), couch = mean(a.couch.prob), cup = mean(a.cup.prob), dog = mean(a.dog.prob), fish = mean(a.fish.prob), house = mean(a.house.prob), person = mean(a.person.prob), phone = mean(a.phone.prob), rabbit = mean(a.rabbit.prob), tree = mean(a.tree.prob), airplane = mean(an.airplane.prob))
 
confusions_melt = melt(confusions)
confusions_melt$target_category = factor(confusions_melt$category_short, levels = c("person" ,"bird", "rabbit", "dog","fish","tree","car","bike","airplane","boat","bowl","cup","phone", "couch","chair","house"))

confusions_melt$guessed_category = factor(confusions_melt$variable, levels = c("person" ,"bird", "rabbit", "dog","fish","tree","car","bike","airplane","boat","bowl","cup","phone", "couch","chair","house"))  

return(confusions_melt)
}
```

## Making confusion matrixes
```{r}
dir.create('plots')

meta_incorrect <- meta %>%
  filter(image_scores==1)

target_ages=c(2,3,4,5,6,7,8,9,10)
for (target_age in target_ages) {
  this_age_confusions = makeConfusions(meta_incorrect, target_age)
  (age_plot = ggplot(data = this_age_confusions, aes(x=guessed_category, y=target_category, fill=value)) + 
  geom_tile() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 1, 
  size = 12, hjust = 1), axis.text.y = element_text(angle = 0,
  size = 12, hjust = 1)) + 
  coord_fixed() + 
  scale_fill_viridis(option="D",limits=c(0, .1))) 
  
  ggsave(paste0('plots','/','Age',target_age,'confusion_matrix.png'),age_plot) 
}

```


### Merge with mongodb database outputs (stroke count, duration, etc.)
Now should be able to look at target label probabilties for each image as a function of all of these other factors
```{r}
d <- read.csv('mongodb-output/MuseumStation_AllDescriptives_20780_images_final_cdm_run_v3.csv') %>%
  as.tibble() %>%
  left_join(meta) %>% # should join on session_id, category, age -- combination of which is unique identifier for an image
  filter(!is.na(target_label_prob)) # if intermediate file, only look where we have data

## we only have meta data for those in cdm_run_v3, and we ran some classifications on cdm_run_v2 -- so mismatch here.
# test_meta <- meta %>%
#   filter(!(session_id %in% mongodb_meta$session_id)) 
```

## Plot data before averaging to get a sense of the distributions
### Target label probs for each category; dots colored by whether it was correctly classified
```{r}
ggplot(d, aes(age_numeric,target_label_prob, col=image_scores)) +
  theme_few() + 
  geom_jitter(alpha=.2, height=0, width=.3) +
  geom_smooth(span=10, col='dark grey') + 
  # scale_color_viridis(option="B") + 
  theme(legend.position = "none") + 
  facet_wrap(~category) +
  labs(y = 'Correct label probability', x = 'Age')
```

### Plot number of strokes x probability of target class 
```{r}
ggplot(d, aes(num_strokes,log(target_label_prob), color=image_scores)) +
  geom_point(alpha=.5) +
  theme_few() + 
  geom_smooth(method='lm') +
  xlim(c(0,50)) + 
  facet_wrap(~category)
```

### Plot mean intensity x probability of target class 
```{r}
ggplot(d, aes(mean_intensity,target_label_prob, color=image_scores)) +
  geom_point(alpha=.5) +
  theme_few() + 
  geom_smooth(method='lm') +
  facet_wrap(~category)
```

### Plot draw duration x probability of target class 
```{r}
ggplot(d, aes(draw_duration_old,target_label_prob, color=image_scores, names = "recognized or not")) +
  geom_point(alpha=.5) +
  theme_few() + 
  geom_smooth(method='lm') +
  facet_wrap(~category) +
  labs(x='Time spent drawing', y='Log probability', color="correctly classified?")
```



### Intensity vs. strokes by age
```{r}
ggplot(d, aes(mean_intensity,num_strokes)) +
  geom_point(alpha=.5) +
  theme_few() + 
  geom_smooth(method='lm') +
  facet_wrap(~age_numeric) +
  ylim(c(0,50)) + ## some crazy outliers here, probably scribbles we didn't catch?
  labs(x='Ink', y='Num strokes')
```



## Compute CIs and look at trends across conditions.
### How does classification accuracy change with age?
```{r}
cor_by_age <- d %>%
  group_by(age_numeric,category) %>%
  summarize(avg_cor = mean(image_scores)) %>%
  group_by(age_numeric) %>%
  multi_boot_standard(col = "avg_cor")  

(cor_by_age_plot = ggplot(cor_by_age, aes(age_numeric,mean, color=age_numeric)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  theme_few(base_size = 18) + 
  labs(x='Age', y='Average drawings recognized') +
  scale_color_viridis(option="D") + 
  theme(legend.position = "none") + 
  geom_smooth(col='grey',span=10))

ggsave('plots-nov26/cor_by_age.png',cor_by_age_plot, width = 6, height = 3)
```

### How does classification probabitlies change with age?
```{r}

prob_by_age <- d %>%
  group_by(age_numeric,category) %>%
  summarize(avg_prob = mean(target_label_prob)) %>%
  group_by(age_numeric) %>%
  multi_boot_standard(col = "avg_prob")  

(prob_by_age_plot = ggplot(prob_by_age, aes(age_numeric,mean, color=age_numeric)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  theme_few() + 
  labs(x='Age', y='Avg target probabilitiy') +
  scale_color_viridis(option="D") + 
  theme(legend.position = "none") + 
  geom_smooth(col='grey',span=10))

ggsave('plots-nov26/prob_by_age.png',prob_by_age_plot, width = 6, height = 3)

```

### How do our covariates change with age? Compute CIs and plot next to accuracy.
```{r}
base_size_chosen=16

cor_by_age_plot_A = ggplot(cor_by_age, aes(age_numeric,mean, color=age_numeric)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age', y='Classification accuracy') +
  scale_color_viridis(option="D") + 
  theme(legend.position = "none") + 
  geom_smooth(col='grey',span=10) +
  ggtitle('A')

draw_duration <- d %>%
  group_by(age_numeric,category) %>%
  summarize(avg_num_strokes = mean(num_strokes), avg_draw_duration = mean(draw_duration_old), avg_intensity = mean(mean_intensity)) %>%
  group_by(age_numeric) %>%
  multi_boot_standard(col = "avg_draw_duration") %>%
  mutate(covariate = 'draw_duration')

num_strokes <- d %>%
  group_by(age_numeric,category) %>%
  summarize(avg_num_strokes = mean(num_strokes), avg_draw_duration = mean(draw_duration_old), avg_intensity = mean(mean_intensity)) %>%
  group_by(age_numeric) %>%
  multi_boot_standard(col = "avg_num_strokes")  %>%
  mutate(covariate = 'num_strokes')

avg_intensity <- d %>%
  group_by(age_numeric,category) %>%
  summarize(avg_num_strokes = mean(num_strokes), avg_draw_duration = mean(draw_duration_old), avg_intensity = mean(mean_intensity)) %>%
  group_by(age_numeric) %>%
  multi_boot_standard(col = "avg_intensity")  %>%
  mutate(covariate = 'intensity')

###
p1=ggplot(draw_duration, aes(age_numeric,mean, color=age_numeric)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Draw duration') +
  scale_color_viridis(option="D") +
  theme(legend.position = "none") + 
  geom_smooth(col='grey', span = 10) +
  ggtitle('B')

p2=ggplot(avg_intensity, aes(age_numeric,mean, color=age_numeric)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Ink used') +
  scale_color_viridis(option="D") +
  theme(legend.position = "none") + 
  geom_smooth(col='grey', span = 10)  +
  ggtitle('C')

p3=ggplot(num_strokes, aes(age_numeric,mean, color=age_numeric)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Num Strokes') +
  scale_color_viridis(option="D") +
  theme(legend.position = "none") + 
  geom_smooth(col='grey', span = 10)  +
  ggtitle('D')

compiledPlot = ggarrange(cor_by_age_plot_A,p1,p2,p3, nrow = 1)
# dir.create('plots-nov26')
ggsave('plots-nov26/correct_and_covariates_by_age.png',compiledPlot, width = 11, height = 4)

```

### How do these results hold up for each category that was drawn? Examine for accuracy.

```{r}
category_by_age_scores <- d %>%
  group_by(category,age_numeric) %>%
  multi_boot_standard(col="image_scores")

(category_by_age_scores_plot <- ggplot(category_by_age_scores, aes(age_numeric,mean, col=age_numeric)) +
  theme_few() + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_smooth(span=10, col='dark grey') + 
  scale_color_viridis(option="D") + 
  theme(legend.position = "none") + 
  facet_wrap(~category) +
  labs(y = 'Average classification accuracy', x = 'Age'))

ggsave('plots-nov26/category_by_age_scores.png', category_by_age_scores_plot, width = 10, height = 8 )

```

### How do these results hold up for each category that was drawn? Examine for target category probabilities.

```{r}
category_by_age_probs <- d %>%
  group_by(category,age_numeric) %>%
  multi_boot_standard(col="target_label_prob")

ggplot(category_by_age_probs, aes(age_numeric,mean, col=age_numeric)) +
  theme_few() + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_smooth(span=10, col='dark grey') + 
  scale_color_viridis(option="D") + 
  theme(legend.position = "none") + 
  facet_wrap(~category) +
  labs(y = 'Correct label probability', x = 'Age')
```


#### Look at increases in confidence only for drawings that were correctly classified.
```{r}
category_by_age_probs_cor_only <- d %>%
  filter(image_scores == 1) %>%
  group_by(category,age_numeric) %>%
  multi_boot_standard(col="target_label_prob")

category_by_age_probs_cor_only_plot <- ggplot(category_by_age_probs_cor_only, aes(age_numeric,mean, col=age_numeric)) +
  theme_few() + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_smooth(span=10, col='dark grey') + 
  scale_color_viridis(option="D") + 
  theme(legend.position = "none") + 
  facet_wrap(~category) +
  labs(y = 'Correct label probability', x = 'Age')

ggsave('plots-nov26/category_by_age_probs_corr_only.png', category_by_age_probs_cor_only_plot, width = 10, height = 8 )

```




  
## Inferential stats
### Generalized linear mixed models on accuracy all covariates 
```{r}
mod_covariates <- glmer(image_scores ~ scale(age_numeric) +
                          scale(draw_duration_old) +
                          scale(mean_intensity) +
                          scale(num_strokes) +
                        (1|session_id) +
                        (1|category),
      data = d,
      family = "binomial")

kable(summary(mod_covariates)$coef, digits = 3)
```

#### Visualize predictions 
```{r}
predicted_df = data.frame(glmer_predictions = predict(mod_covariates, d), age=d$age_numeric, category=d$category)

(predicted_accuracy <- ggplot(data = predicted_df, aes(x=age, y=glmer_predictions, col=age)) +
  scale_color_viridis()  +
  theme_few() + 
  geom_jitter(alpha=.1, width=.2, height=0) + 
  stat_smooth(col='grey', method='lm') +
  theme(legend.position = "none") + 
  scale_x_discrete(limits=c(2,3,4,5,6,7,8,9,10)) +
  labs(x = 'Age', y = 'Predicted accuracy of actual category'))

ggsave('plots-nov26/predicted_accuracy.png',predicted_accuracy, width = 6, height = 4 )

```



### Generalized linear mixed model on category probabilities with all covariates 
```{r}
mod_covariates_prob <- glmer(target_label_prob ~ scale(age_numeric) +
                          scale(draw_duration_old) +
                          scale(mean_intensity) +
                          scale(num_strokes) +
                        (1|session_id) +
                        (1|category),
      data = d)

kable(summary(mod_covariates_prob)$coef, digits = 3)
```

#### Visualize predictions by age
```{r}

predicted_df = data.frame(glmer_predictions_prob = predict(mod_covariates_prob, d), age=d$age_numeric, category=d$category)

## Model prediction lines overlaid on raw data fed to the model
(predicted_probs <- ggplot(data = predicted_df, aes(x=age, y=glmer_predictions_prob, col=age)) +
  scale_color_viridis()  +
  theme_few() + 
  geom_jitter(alpha=.1, width=.2, height=0) + 
  stat_smooth(col='grey', method='lm') +
  theme(legend.position = "none") + 
  scale_x_discrete(limits=c(2,3,4,5,6,7,8,9,10)) +
  labs(x = 'Age', y = 'Predicted probability of actual category'))

ggsave('plots-nov26/predicted_probs.png',predicted_probs, width = 6, height = 4 )

```

### Run model on probabilities only when it was classified correctly
E.g., is there an increase in confidence independent of an increase in accuracy of the classifier?
```{r}
d_correct <- d %>%
  filter(image_scores == 1)

mod_covariates_correct_only <- glmer(target_label_prob ~ scale(age_numeric) +
                          scale(draw_duration_old) +
                          scale(mean_intensity) +
                          scale(num_strokes) +
                        (1|session_id) +
                        (1|category),
      data = d_correct)
modelOut=summary(mod_covariates_correct_only)
kable(summary(mod_covariates_correct_only)$coef, digits = 3)

```


##Render out subsets of classifications by classification scores
#### Set parameters
```{r}
### Set parameters first
categories = unique(meta$category)
##
upper_thresholds=c(1,.85,.65,.45,.25,.05)
lower_thresholds=c(.95,.80,.60,.40,.20,0)
##
age_thres = 0
dir_name = 'subset_classification_examples_test'
dir.create(dir_name)
```
### Render out random sample with these parameters
```{r eval=FALSE}
##
for (this_category in categories){
  dir.create(file.path(paste(dir_name,'/',this_category,sep="")))
  thres_count=0
  
  for (upper in upper_thresholds) {
    thres_count = thres_count + 1
    lower = lower_thresholds[thres_count]
    subset <- meta %>%
      filter(age_numeric > age_thres) %>%
      group_by(category) %>%
      mutate(upper_thres = quantile(target_label_prob, upper, na.rm = TRUE)) %>%
      mutate(lower_thres = quantile(target_label_prob, lower, na.rm = TRUE)) %>%
      filter(category == this_category) %>%
      filter(target_label_prob > lower_thres & target_label_prob < upper_thres) %>%
      sample_n(2) %>%
      mutate(image_path = paste('srcd-features/museumstation_sketches/',category,'/',image_name,sep="")) %>%
      mutate(new_image_path = paste(dir_name,'/',this_category,'/',
                                    round(target_label_prob,4),image_name,sep=""))
    
    file.copy(subset$image_path, subset$new_image_path)
  }
}

### Make montages of these randomly sampled sketches for use in diagrams
dir.create(paste0(dir_name,'/montages/'))
for (this_category in categories){
  image_read(dir(paste(dir_name, "/",this_category,sep=""), full.names = TRUE)) %>%
  image_append(stack = FALSE) %>%
    image_write(file.path(paste0(dir_name,"/montages/", this_category,".png")))
}

```
#### Correct only
```{r eval=FALSE}
##
age_thres = 4
dir_name = 'subset_classification_examples_ages4_10_correct_only'
dir.create(dir_name)

##
for (this_category in categories){
  dir.create(file.path(paste(dir_name,'/',this_category,sep="")))
  thres_count=0
  
  for (upper in upper_thresholds) {
    thres_count = thres_count + 1
    lower = lower_thresholds[thres_count]
    subset <- meta %>%
      filter(age_numeric > age_thres) %>%
      filter(image_scores==1 ) %>%
      group_by(category) %>%
      mutate(upper_thres = quantile(target_label_prob, upper, na.rm = TRUE)) %>%
      mutate(lower_thres = quantile(target_label_prob, lower, na.rm = TRUE)) %>%
      filter(category == this_category) %>%
      filter(target_label_prob > lower_thres & target_label_prob < upper_thres) %>%
      sample_n(2) %>%
      mutate(image_path = paste('srcd-features/museumstation_sketches/',category,'/',image_name,sep="")) %>%
      mutate(new_image_path = paste(dir_name,'/',this_category,'/',
                                    round(target_label_prob,4),image_name,sep=""))
    
    file.copy(subset$image_path, subset$new_image_path)
  }
}

### Make montages of these randomly sampled sketches for use in diagrams
dir.create(paste0(dir_name,'/montages/'))
for (this_category in categories){
  image_read(dir(paste(dir_name, "/",this_category,sep=""), full.names = TRUE)) %>%
  image_append(stack = FALSE) %>%
    image_write(file.path(paste0(dir_name,"/montages/", this_category,".png")))
}

```


```{r include=FALSE}
### Diffeent divisions of category probabilities... not that useful with imbalanced sets, come back to?

# d$summed_probs = d$a.bike.prob + d$a.bird.prob + d$a.boat.prob + d$a.bowl.prob + d$a.car.prob + d$a.chair.prob + d$a.couch.prob + d$a.cup.prob + d$a.dog.prob + d$a.fish.prob + d$a.house.prob  + d$a.person.prob + d$a.phone.prob + d$a.rabbit.prob + d$a.tree.prob + d$an.airplane.prob

# d$animate_prob =  d$a.bird.prob + d$a.dog.prob + d$a.fish.prob + d$a.rabbit.prob 
# d$small_prob = d$a.bowl.prob + d$a.cup.prob + d$a.phone.prob
# d$furniture_prob = d$a.chair.prob + d$a.couch.prob
# d$vehicle_prob = d$a.boat.prob + d$a.car.prob + d$a.bike.prob + d$a.car.prob + d$an.airplane.prob

# animate_list = c('a bird','a dog','a fish','a rabbit')
# d <- d %>%
#   mutate(is_animate = (category %in% animate_list))?

# ggplot(d, aes(age_numeric,log(target_label_prob), color=image_scores)) +
#   geom_point(alpha=.5) +
#   theme_few() + 
#   geom_smooth()  +
#   facet_wrap(~category) +
#   labs(x='Age', y='Log probability', color="correctly classified?")
  
# ggplot(d, aes(age_numeric,log(animate_prob), color=image_scores)) +
#   geom_point(alpha=.5) +
#   theme_few() +
#   geom_boxplot(aes(groups=age_numeric)) +
#   facet_wrap(~category) +
#   labs(x='Age', y='Log probability', color="correctly classified?")
# # 
# ggplot(d, aes(age_numeric,log(vehicle_prob))) +
#   theme_few() + 
#   geom_boxplot(aes(group=age_numeric)) +
#   facet_wrap(~category) +
#   labs(x='Age', y='Log probability', color="correctly classified?")
# 
# ggplot(d, aes(age_numeric,log(small_prob))) +
#   theme_few() + 
#   geom_boxplot(aes(group=age_numeric)) +
#   facet_wrap(~category) +
#   labs(x='Age', y='Log probability', color="correctly classified?")
```


