---
title: "MuseumStation Preprocessing"
author: ""
date: "9/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(assertthat)
library(knitr)
library(here)
library(lubridate)
```


## Select cdm run we are filtering and set paths accordingly
```{r}
run_name = 'cdm_run_v7'

# input paths
drawing_path = here::here('data/drawings',run_name)
full_set_drawing_path = here::here('data/drawings',run_name, 'sketches_full_dataset')
descriptives_path =  here::here('data/drawings',run_name,'sketches_descriptives')

# create output paths
filtered_dataset_path =  fs::path(drawing_path,'filtered_dataset')
dir.create(filtered_dataset_path)

filtered_descriptives_path = fs::path(drawing_path,'filtered_dataset_descriptives')
dir.create(filtered_descriptives_path)
```

## List all of the drawings in the rendered dataset 
```{r}
all_drawings = list.files(path=full_set_drawing_path, pattern = ".png$", recursive = TRUE)

all_drawings = as.tibble(all_drawings)  %>%
    rename(sketchName = value) %>%
    mutate(fileNameShort = str_split_fixed(sketchName,"/",2)[,2]) 

```

## If cdm_run_v4, some of these have already been examined...
So filter out drawings that were already filtered for the cogsci paper
```{r}
if (run_name == 'cdm_run_v4'){

  subset_drawing_path = here::here('data/drawings','subset_cogsci_2019_dataset')
  subset_drawings = list.files(path=subset_drawing_path, pattern = ".png$", recursive = TRUE)
  subset_drawings = as.tibble(subset_drawings) %>%
    rename(sketchName = value) %>%
    mutate(fileNameShort = str_split_fixed(sketchName,"/",2)[,2]) 

  all_drawings <- all_drawings %>%
    filter(!fileNameShort %in% subset_drawings$fileNameShort) 
}
```

## Load csvs with descriptives
```{r}
descriptives_file = list.files(path = descriptives_path, pattern = ".csv$")

descriptives = read_csv(fs::path(descriptives_path, descriptives_file), col_names = TRUE) %>%
  mutate(fileNameShort = sapply(str_split(filename, '/'),tail,1L)) %>%
  mutate(draw_duration_new = as.numeric(draw_duration_new)) %>%
  select(-X1)

```

## How many drawings do we have before exclusion (not counting practice trials)?
```{r}
#
practice_categories = c('shape','this circle','square','this square','something you love')
extra_prompt = c('something you love')

# 
raw_drawing_count <- descriptives %>%
  full_join(descriptives) %>%
  filter(!category %in% practice_categories) %>%
  filter(!category %in% extra_prompt) 
  
age_by_category <- raw_drawing_count %>%
  group_by(category, age) %>%
  summarize(num_drawings = length(unique(filename))) %>%
  kable()


drawing_count_total = length(unique(raw_drawing_count$filename))
```
There are `r drawing_count_total` drawings total in `r run_name`

## Load manual exclusions from previous filtering (incomplete)
```{r}
# only for cdm runs 3,4,5
exclude_path = here::here('data','images_to_exclude')
exclude_files = dir(exclude_path)
count_file = 0
for (e in exclude_files) {
  count_file = count_file +1
  these_exclusions = read_csv(file = fs::path(exclude_path,e), col_names = FALSE) %>%
    as_tibble() 

  if (count_file == 1){
    all_exclusions = these_exclusions
  }
  else {
    all_exclusions = all_exclusions %>%
      full_join(these_exclusions)
    
  }
    
}
all_exclusions <- all_exclusions %>%
  rename(fileNameShort = X1) %>%
  mutate(version = str_split_fixed(fileNameShort,'_',4)[,4]) %>%
  mutate(version = substring(version,1,10)) %>%
  filter(version %in% c('cdm_run_v3','cdm_run_v4','cdm_run_v5')) %>% # some manually filtered drawings from pilot runs that shouldn't be included in counts
  
all_exclusions <- all_exclusions %>%  
  mutate(age_temp = str_split_fixed(fileNameShort, 'age',3)[,2])%>%
  mutate(age_numeric = as.numeric(str_split_fixed(age_temp,'_',2)[,1]))


# filter out manually excluded drawings
descriptives_filtered_v1 <- descriptives %>%
  filter(!fileNameShort %in% all_exclusions$fileNameShort)%>%
  mutate(version = str_split_fixed(fileNameShort,'_',4)[,4]) %>%
  mutate(version = substring(version,1,10)) %>%
  mutate(age_temp = str_split_fixed(fileNameShort, 'age',3)[,2])

# output how many we filtered
excluded_files <- descriptives %>%
  filter(fileNameShort %in% all_exclusions$fileNameShort) 

num_drawings_manually_excluded = length(excluded_files$fileNameShort)
```
There were `r num_drawings_manually_excluded` in `r run_name` that were manually excluded based on previous filtering by the authors for another purpose (recognition games or cogsci2019 filtering).


```{r}
all_exclusions_by_age <- all_exclusions %>%
  group_by(age_numeric) %>%
  summarize(count_drawings_excluded = n())
```


## Filter those drawings and make nicer columns
```{r}
 
filtered_drawings <- all_drawings %>% 
  filter(!(fileNameShort=="")) %>% 
  left_join(descriptives_filtered_v1, by=c('fileNameShort')) %>%
  filter(!is.na(trial_num)) %>% # only consider image paths with descriptives...
  mutate(fullPath = paste(full_set_drawing_path, '/', sketchName,sep="")) %>%
  select(-sketchName)
```

## Filtering pass 1:
### Grab images with weird intensities and save them out for manual insepction; all are excluded.
```{r}
light_thres = quantile(filtered_drawings$mean_intensity,.01)
dark_thres = quantile(filtered_drawings$mean_intensity,.99)

dark_drawings <- filtered_drawings %>%
  filter(mean_intensity > dark_thres) 
  
almost_blank <- filtered_drawings %>%
  filter(mean_intensity < light_thres)
```

```{r}
dir.create(fs::path(drawing_path,'sketches_subsets_inspection'))
dark_sketches_dir = fs::path(drawing_path,'sketches_subsets_inspection/maybe_exclude_dark_sketches') 
light_sketches_dir = fs::path(drawing_path,'sketches_subsets_inspection/maybe_exclude_light_sketches')

# dir.create(dark_sketches_dir)
# dir.create(light_sketches_dir)

# file.copy(dark_drawings$fullPath, dark_sketches_dir)
# file.copy(almost_blank$fullPath, light_sketches_dir)
```


### After manually going through drawings and making new csv file, exclude those drawings
```{r}
## loading drawings to exclude based on manual exclusions
# drawings_to_exclude_2 = read_csv(file = 'images_to_exclude/images_to_exclude_scribbles_dark_light.txt', col_names = FALSE)
# drawings_to_exclude_2 = as.tibble(drawings_to_exclude_2)
# 
# ## copy all drawings into one directory
# descriptives_filtered_v3 <- descriptives_filtered_v2 %>%
#   filter(!fileNameShort %in% drawings_to_exclude_2$X1) 

# filtered_sketches_dir = 'filtered_sketches'
# dir.create(filtered_sketches_dir)
# file.copy(descriptives_full_filtered$fullPath, filtered_sketches_dir)
```

```{r}
## loading drawings to exclude based on manual exclusions based on rest of dataset
# drawings_to_exclude_3 = read_csv(file = 'images_to_exclude/images_to_exclude_manual.txt', col_names = FALSE)
# drawings_to_exclude_3 = as.tibble(drawings_to_exclude_3)
```
### Exclude last round and clean up datasets
```{r}
## Clean up -- exclude practice categories, recode age as numeric, make filenames w/o spaces
practice_categories = c('shape','this circle','square','this square','something you love')
extra_prompt = c('something you love')

# clean up dataset and filter out manual exclusions
filtered_drawings_objects <- filtered_drawings %>%
  filter(!fileNameShort %in% almost_blank$fileNameShort) %>% 
  filter(!fileNameShort %in% dark_drawings$fileNameShort) %>% 
  mutate(age_numeric = as.numeric(str_split_fixed(age,'age',2)[,2])) %>%
  mutate(fileNameShortNew = str_split_fixed(fileNameShort," ",2)[,2]) %>%
  mutate(draw_duration_new = as.numeric(is.na(draw_duration_new))) %>%
  filter(!category %in% practice_categories) %>%
  filter(!category %in% extra_prompt) 

## now only get practice trials for people who made it into the full dataset
obj_session_ids = unique(filtered_drawings_objects$session_id)
practice_shapes_filtered <- filtered_drawings %>%
  filter(!fileNameShort %in% almost_blank$fileNameShort) %>% 
  filter(!fileNameShort %in% dark_drawings$fileNameShort) %>% 
  mutate(age_numeric = as.numeric(str_split_fixed(age,'age',2)[,2])) %>%
  mutate(fileNameShortNew = str_split_fixed(fileNameShort," ",2)[,2]) %>%
  mutate(draw_duration_new = as.numeric(is.na(draw_duration_new))) %>%
  filter(category %in% practice_categories) %>%
  filter(!category %in% extra_prompt) %>%
  filter(session_id %in% obj_session_ids) 

all_drawings_filtered <- filtered_drawings_objects %>%
  full_join(practice_shapes_filtered)
```


#### Hm, there are some drawings with lots of strokes -- lets look at them.
```{r}
# look at the crazy drawings
high_strokes <- all_drawings_filtered %>%
  filter(num_strokes > 50)

dir.create(fs::path(drawing_path,'sketches_subsets_inspection/images_many_strokes'))
file.copy(high_strokes$fullPath,fs::path(drawing_path,'sketches_subsets_inspection/images_many_strokes'))
```




## How many sketches are we left with in each age / category?
```{r}
category_by_age <- all_drawings_filtered %>%
  group_by(category,age_numeric) %>%
  summarize(countImages = n())

ggplot(category_by_age,aes(age_numeric,countImages,color=age_numeric)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(~category)

```


### Save it out
```{r}
# all output csvs
write.csv(all_drawings_filtered,fs::path(filtered_descriptives_path,paste0(run_name, '_filtered_', today(), '.csv'))) 

# only objects
write.csv(filtered_drawings_objects,fs::path(filtered_descriptives_path,paste0(run_name, 'objects_filtered_', today(), '.csv'))) 
```

### Render out new copies of filtered datasets
```{r}


file.copy(from = file.path(filtered_drawings_objects$fullPath), to=file.path(filtered_dataset_path, filtered_drawings_objects$fileNameShortNew))

```



```{r}
# debugging code below -- 
# was originally merging on 'X1' -- causing a few duplicates! weird. 

# what <- read_csv(fs::path(filtered_descriptives_path, 'cdm_run_v5objects_filtered_2020-09-01.csv'))
# duplicates <- filtered_drawings_objects %>%
#   group_by(fileNameShort) %>%
#   mutate(duplicate = n()) %>%
#   filter(duplicate>1)
# 
# check_path = fs::path(drawing_path, 'sketches_subsets_inspection','duplicates')
# dir.create(check_path)
# 
# file.copy(from = file.path(filtered_dataset_path,duplicates$fileNameShortNew),to=file.path(check_path, duplicates$fileNameShortNew))
# 
# one_image <- duplicates %>%
#   filter(fileNameShort == duplicates$fileNameShort[1])


```