---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}

<!-- ### Category similarity analyses -->
<!-- Next, we explored which categories generated representations in FC7 that were  more or less similar between younger children vs. adults and between older children vs. adults (see Figure \ref{fig:simpleCorr}). Overall, we found a good deal of variability; for some categories, children's and adult's drawings generated feature representations that were relatively dissimilar in this final layer of the network (e.g., couches, shoes) while others generated very similar feature representations (e.g., flowers, chairs). -->

<!-- ```{r echo=FALSE, include=FALSE} -->
<!-- c <- read_csv("vggOutputs/FeatureCorrelationsByClass.csv")   -->
<!-- c_plot <- c %>% -->
<!--     gather(key = ageGroup, value = corr, `Correlations-Older`, `Correlations-Younger`) %>% -->
<!--     gather(key = cohortLabels, value = label, `Labels-Older`, `Labels-Younger`) %>% -->
<!--     mutate(label = fct_reorder(label, corr))  %>% # for order in plot -->
<!--     select(-`Correlations-AllKids`, -`Labels-AllKids`) # cleanup -->

<!-- ``` -->

<!-- ```{r simpleCorr, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.label="headcam", fig.cap = "Spearman's correlation between children's and adults sketches in layer FC7 for each object category."} -->

<!-- # to do:  -->
<!-- # legend is pretty big relative to plot -->

<!-- ggplot(c_plot, aes(x = label, y = corr, fill=ageGroup)) +  -->
<!--   geom_bar(stat="identity",position="dodge") + -->
<!--   theme_bw()+ -->
<!--   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + -->
<!--   theme(legend.direction = "horizontal", legend.position="bottom", text = element_text(size=6)) + -->
<!--   labs(y = " Corr. with adults (FC7)", x = "Object category") + -->
<!--   scale_fill_brewer(palette="Paired","Age group", labels=c( "7-10 yrs.","3-6 yrs."),direction=-1) ## direction = -1 allows colors to be the same as with other  -->

<!-- ``` -->
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
