---
title: "Drawing_analyses"
author: "Bria Long"
date: "9/23/2020"
output: html_document
---

# Libraries and data
```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(assertthat)
library(ggthemes)
library(egg)
library(viridis)
library(lme4)
library(lmerTest)
library(MuMIn)
library(langcog)
```

## Load metadata
```{r}
all_meta <- read_csv(file = here::here('data/drawings/stringent_cleaned_dataset_meta/all_object_metadata_cleaned.csv')) %>%
  as_tibble() %>%
  mutate(category = str_split_fixed(category,' ',2)[,2]) %>%
  mutate(category = str_replace(category,' ','.'))  # ice cream
```

### Basic descriptives of filtered set
```{r}
num_subs = length(unique(all_meta$session_id))
```

The final, filtered dataset of N=`r length(unique(all_meta$filename))`  drawings from `r length(unique(all_meta$category))` categories from `r num_subs` children who were on average `r mean(all_meta$age_numeric)`years of age (range 3-10 years). 

### Load frequency ratings
```{r}
frequency = read_csv(file = here::here('data/surveys/drawing_experience/preprocessed/Category_frequency_survey.csv')) 
```

To assess this, `r length(unique(frequency$subject_id))` parents of children aged 3-10 years filled out a survey asking about the frequency with with their children drew the categories in the dataset.

```{r}
count_by_age <- frequency %>%
  group_by(childs_age) %>%
  dplyr::summarize(num_surveys = length(unique(subject_id)))
```

```{r}
freq_by_category <- frequency %>%
  # filter(childs_age > 2) %>%
  mutate(category = str_split_fixed(category,' ',2)[,2]) %>%
  mutate(category = str_replace(category,' ','.')) %>%
  filter(category %in% all_meta$category) %>%
  group_by(category) %>%
  summarize(drawing_frequency = mean(often_drawn_rating)) %>%
  mutate(above_median_freq = drawing_frequency > median(drawing_frequency)) 

# write_csv(freq_by_category, here::here('data/surveys/drawing_experience/preprocessed/freq_by_category.csv'))


```

### Load tracing data
```{r}
all_tracings <- read_csv(here('data/tracing/rated_all_museumstation_filtered.csv'))%>%
  select(-X1, -X)

## Make averages for joining
by_subject_tracing_avg <- all_tracings %>%
  distinct(session_id, category, age, rating) %>% 
  group_by(session_id) %>%
  summarize(avg_tracing_rating = mean(rating))
```

### Load animacy/size (hardcoding)
```{r}
animacy_csv <- read_csv(here::here('data/drawings/category_metadata/animacy.csv')) %>%
  as_tibble() %>%
  mutate(animacy_size = case_when(animacy == '0' & size=='0' ~ 2,
                                  animacy == '0' & size=='1' ~ 1,
                                  animacy == '1' & size=='0' ~ 3,
                                  animacy == '1' & size=='1' ~ 4))

```


### Load classification data
```{r}
num_batches=232
reg_string = 'C_0.1_T_0.1'
classification_data <- read.csv(here::here('data','compiled_classifications/',paste0(reg_string, 'batchtotal_',as.character(num_batches),'.csv'))) %>%
  mutate(session_id = paste('cdm_',session_id,sep="")) %>%
  mutate(age_numeric = age) %>%
  mutate(age = paste('age',age,sep="")) %>%
  mutate(age = as.factor(age)) %>%
  mutate(category = target_label) %>%
  mutate(image_name = paste(target_label,'_sketch_', age,'_', session_id,'.png',sep="")) %>%
  select(-X)  %>%
  mutate(category = str_replace(category,' ','.'))  # ice cream = ice.cream


```


## Join meta data, drawing frequnecy, and classification data
```{r}
d <- classification_data %>%
  mutate(correct_or_not = as.logical(correct_or_not)) %>%
  gather(key = 'class', value = 'prob', contains('prob')) %>%
  mutate(class = str_split_fixed(class, '_prob',2)[,1]) %>%
  group_by(image_name, age, category, correct_or_not, session_id, age_numeric) %>%
  summarize(denom = sum(prob), target_label_prob = prob[class==category], log_odds = log(target_label_prob / (denom - target_label_prob))) %>%
  rename(filename = image_name) %>%
  left_join(all_meta, by=c("filename", "category", "age_numeric","session_id")) %>%
  mutate(draw_duration = draw_duration_old) %>% # using end of last stroke - end of first stroke (is 0 for one stroke drawings)
  mutate(run = substr(session_id,0,10)) %>%
  left_join(freq_by_category)

```

## Join tracing ratings
```{r}
d <- d %>%
  left_join(by_subject_tracing_avg)
```


### Asserts to check all the joins
```{r}
# weird things were happening with category matching, check
assert_that(length(unique(d$filename)) == length(unique(classification_data$image_name)))

# every drawing should have all of these, regardless
assert_that(sum(is.na(d$age_numeric))==0)
assert_that(sum(is.na(d$category))==0)
assert_that(sum(is.na(d$correct_or_not))==0)

missing_meta <- d %>%
  filter(is.na(num_strokes))

assert_that(length(missing_meta$filename)==0)
```

# Main Figures
## Figure 2A: Classification by age
```{r descriptives-across-age}
## first summarize data  
cor_by_age <- d %>%
  group_by(age_numeric,category) %>%
  summarize(avg_cor = mean(correct_or_not)) %>%
  group_by(age_numeric) %>%
  multi_boot_standard(col = "avg_cor")  

cor_by_category <- d %>%
  group_by(age_numeric,category) %>%
  dplyr::summarize(mean = mean(correct_or_not), num_drawings = n()) %>%
  group_by(age_numeric)
```

```{r}
base_size_chosen=10
smooth_alpha=.01
ggplot(cor_by_age, aes(age_numeric,mean*100, col=age_numeric)) +  
  geom_jitter(data=cor_by_category, width=.1, height=0, alpha=.2) +
  geom_pointrange(aes(y=mean*100, ymin = ci_lower*100, ymax = ci_upper*100)) +
  geom_smooth(alpha=smooth_alpha, color='grey', span=10) +
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age of child drawing (yrs)', y='Drawing classification accuracy') +
  scale_x_continuous(breaks = seq(2,10,1)) + 
  theme(legend.position = "none", aspect.ratio = 1) +
  scale_color_viridis(option="D", breaks=seq(2,10,1)) +
  geom_hline(yintercept = 1/48, linetype="dashed", color="grey") 

ggsave('figures/cor_by_category.pdf', width=3, height=3, units='in')
```


## Figure 2B: Changes in log-odds by age group for correctly classified drawings only
```{r}
lo_correct_category_by_age <- d %>%
  filter(correct_or_not==1) %>%
  mutate(category = str_replace(category,'ice.cream','ice cream')) %>%  # ice.cream -> ice_cream
  mutate(age = cut(age_numeric, c(1.9, 5, 8,10.1), labels = c("2-4","5-7","8-10"))) %>%
  group_by(session_id, age,category) %>%
  summarize(avg_cor = mean(log_odds), num_drawings = n()) %>%
  group_by(age, category) %>%
  multi_boot_standard(col = 'avg_cor') %>%
  ungroup () %>%
  mutate(category = fct_reorder(category, mean)) 
```

```{r}
num_classes=48
chance = log(1/num_classes) - log ((num_classes - 1)/num_classes)
base_size_chosen=10
ggplot(lo_correct_category_by_age, aes(x = category, y = mean, col = age)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha=.8, size=.2) +
  coord_flip() +
  theme_few(base_size = base_size_chosen) + 
  labs(y = "Classifier evidence (log odds)", x = "") +
  scale_color_viridis(discrete=TRUE, begin=0, end=.8, name = "Age group") +
  theme(legend.position = c(.8,.25), axis.text.y = element_text(size=5), legend.text = element_text(size=8), legend.background =  element_rect(fill=alpha('white', 0)), aspect.ratio=1) 

ggsave("figures/log_odds_by_category.pdf", units = 'in', height= 3)


```
## Figure 3: Misclassified draiwngs
### Make long form classification data
```{r}
classification_data_long <- classification_data %>%
  mutate(correct_or_not = as.logical(correct_or_not)) %>%
  gather(key = 'class', value = 'prob', contains('prob')) %>%
  mutate(class = str_split_fixed(class, '_prob',2)[,1]) 
```


### Calculate avg prob by category for misclassified
```{r}
confusions_by_age <- classification_data_long %>%
  mutate(drawn_category = category) %>%
  left_join(animacy_csv) %>%
  ungroup() %>%
  filter(correct_or_not==0) %>%
  filter(age_numeric > 2) %>%
  mutate(drawn_category = fct_reorder(drawn_category, animacy_size)) %>%
  mutate(class = factor(class, levels = levels(drawn_category))) %>%
  mutate(age_group = cut(age_numeric, c(2.9, 5, 7,10.1), labels = c("3-4","5-6","7-10"))) %>%
  group_by(age_group, age_numeric, drawn_category, class) %>%
  dplyr::summarize(mean_prob = mean(prob)) 

confusions_by_class <- classification_data_long %>%
  mutate(drawn_category = category) %>%
  left_join(animacy_csv) %>%
  ungroup() %>%
  filter(correct_or_not==0) %>%
  mutate(drawn_category = fct_reorder(drawn_category, animacy_size)) %>%
  mutate(class = factor(class, levels = levels(drawn_category))) %>%
  group_by(drawn_category, class) %>%
  dplyr::summarize(mean_prob = mean(prob)) 

levels(confusions_by_age$drawn_category)

```


### Figure 3A: Confusions by class
```{r}
ggplot(data = confusions_by_class, aes(x=class, y=drawn_category,fill=mean_prob)) + 
  geom_tile() + 
  theme_few(base_size = 12) +
  theme(legend.position = 'left', axis.text.x = element_text(angle = 90,  
  size = 6, vjust=.5, hjust = 1), axis.text.y = element_text(angle = 0,
  size = 6, hjust = 1)) + 
  coord_fixed() + 
  scale_fill_viridis(option="A", limits=c(0,quantile(confusions_by_age$mean_prob,.998)), name = 'Classifier probability')  +
  ylab('Drawn as') +
  xlab('Confused with') 

ggsave('figures/classifier_confusions.pdf', width = 4, height = 5, units = 'in')
```



### Calculate whether animacy/size were correct
```{r}
animacy_size_acc_by_age <- classification_data_long %>%
  mutate(drawn_category = category) %>%
  left_join(animacy_csv %>% select(animacy, size, category), by = c("drawn_category" = "category")) %>%
  ungroup() %>%
  rename(drawn_category_animacy = animacy, drawn_category_size = size) %>%
  left_join(animacy_csv %>% select(animacy, size, category),  by = c("class" = "category")) %>%
  rename(class_animacy = animacy, class_size = size) %>%
  group_by(image_name, drawn_category, age_numeric) %>%
  mutate(max_prob = max(prob), top_class = prob==max_prob)  %>%
  filter(top_class==TRUE) %>%
  mutate(animacy_correct = (drawn_category_animacy == class_animacy)) %>%
  mutate(size_correct = (drawn_category_size == class_size)) 

```

### Calculate animacy correct relative to basline
```{r}
baseline_animacy <- mean(animacy_csv$animacy)
baseline_objects <- 1 - mean(animacy_csv$animacy)

anim_cor_by_category_by_age <- animacy_size_acc_by_age %>%
  filter(correct_or_not==0) %>%
  mutate(drawn_category_animacy = as.factor(drawn_category_animacy))  %>%
  mutate(baseline_chance = case_when(drawn_category_animacy == 0 ~ baseline_objects, 
                                     drawn_category_animacy == 1 ~ baseline_animacy)) %>%
  group_by(age_numeric, drawn_category) %>%
  dplyr::summarize(avg_animacy_correct = mean(animacy_correct) - baseline_chance) %>%
  distinct(age_numeric, avg_animacy_correct, drawn_category)
  
anim_cor_by_age <- anim_cor_by_category_by_age %>%
  group_by(age_numeric) %>%
  multi_boot_standard(col = 'avg_animacy_correct')

```



### Figure 3B: Plot animacy correct by age
```{r}
ggplot(anim_cor_by_age, aes(x=age_numeric,y=mean, color=age_numeric)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha=.8, size=.2) + 
  geom_point(data=anim_cor_by_category_by_age, aes(x=age_numeric, y=avg_animacy_correct), alpha=.1, size=.5) +
  theme_few(base_size = 8) + 
  labs(x='Age', y='Prop. animacy correct') +
  theme(legend.position = "none") +
  # geom_smooth(span=10, alpha=smooth_alpha, color='grey') +
  scale_color_viridis(option="D", discrete=FALSE) +
  geom_hline(yintercept =  0 , linetype="dashed", color="grey") 


ggsave('figures/animacy_classification.pdf', width = 1.5, height = 1.5, units = 'in')


```

```{r}
objects_only <- animacy_csv %>%
  filter(animacy==0)

baseline_big <- mean(objects_only$size)
baseline_small <- 1 - mean(objects_only$size)

size_cor_by_category_by_age <- animacy_size_acc_by_age %>%
  filter(correct_or_not==0) %>%
  filter(drawn_category_animacy==0) %>% #only objects
  mutate(drawn_category_size = as.factor(drawn_category_size))  %>%
  mutate(baseline_chance = case_when(drawn_category_size == 0 ~ baseline_small, 
                                     drawn_category_size == 1 ~ baseline_big)) %>%
  group_by(age_numeric, drawn_category) %>%
  dplyr::summarize(avg_size_correct = mean(size_correct) - baseline_chance) %>%
  distinct(age_numeric, avg_size_correct, drawn_category)

size_cor_by_age <- size_cor_by_category_by_age %>%
  group_by(age_numeric) %>%
  multi_boot_standard(col = 'avg_size_correct')

```

### Figure 3C: Size correct by age
```{r}
ggplot(size_cor_by_age, aes(x=age_numeric,y=mean, color=age_numeric)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha=.8, size=.2) + 
  geom_point(data=size_cor_by_category_by_age, aes(x=age_numeric, y=avg_size_correct), alpha=.1, size=.5) +
  theme_few(base_size = 8) + 
  labs(x='Age', y='Prop. object size correct') +
  theme(legend.position = "none") +
  # geom_smooth(span=10, alpha=smooth_alpha, color='grey') +
  scale_color_viridis(option="D", discrete=FALSE) +
  geom_hline(yintercept =  0 , linetype="dashed", color="grey") 

ggsave('figures/size_classification.pdf', width = 1.5, height = 1.5, units = 'in')
```


# Run inferential statisitics and output
```{r}
# set seed for reproducibility
set.seed(123)
```


## Full model predicting accuracy for all drawings
```{R}
all_covariates_accuracy <- glmer(correct_or_not ~ scale(age_numeric)*scale(drawing_frequency)+scale(avg_tracing_rating) + scale(draw_duration) +
                          scale(mean_intensity) +
                          scale(num_strokes) +
                        (1|session_id) +
                        (1|category),
      data = d, family="binomial",control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e4)))
```

### Table 1
```{R}
xtable::xtable(summary(all_covariates_accuracy)$coef, digits=3, caption = "Model coefficients of a GLMM predicting the recognizability of each drawing (i.e. binary classification scores), including randomintercepts for each category and participant.")

```

# Full model predicting log odds for correctly classified drawings
```{r}
correct_subset <- d %>% 
  filter(correct_or_not==1)

all_covariates_log_odds_corr_only <- lmer(log_odds ~ scale(age_numeric)*scale(drawing_frequency) + scale(avg_tracing_rating) + scale(draw_duration) +
                          scale(mean_intensity) +
                          scale(num_strokes) +
                        (1|session_id) +
                        (1|category),
      data = correct_subset, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e4)))

log_odds_out = summary(all_covariates_log_odds_corr_only)$coef

```

Even for drawings that were correctly classified (near 33\% of the balanced subset of drawings, $N$=`r length(unique(correct_subset$filename))`) there was still a reliable increase in the amount of diagnostic information they contained across age, as measured by the log-odds probability assigned by the logistic-regression classifier to the target category (see \textit{Methods}, \textit{B} = `r round(log_odds_out[2,1],3)` , \textit{SE} = `r round(log_odds_out[2,2],3)`, \textit{df} =  `r round(log_odds_out[2,3],3)`, \textit{t} = `r round(log_odds_out[2,4],3)`, \textit{P} < `r round(log_odds_out[2,5],3)`). Thus, this secondary analysis provides additional support for the account that the age-related improvements reflect gradual changes in children's ability to include diagnostic visual features in their drawings (see Figure \ref{fig:drawing_production}B).  





