---
title: "Drawing-Recognition-Analyses"
author: "Bria Long"
date: "5/8/2019"
output: 
  html_document:
    toc: true
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(ggplot2)
library(assertthat)
library(langcog)
library(viridis)
library(ggthemes)
library(lme4)
library(lmerTest)
```

## Import animalgame & vehiclegame data & import classifications (4 way classification on each set of drawings)
```{r}
animal_game <- read.csv("recognition_data/animalgame_v1_out_may8_final.csv") %>%
  as.tibble() %>%
  select(-X)

vehicle_game <- read.csv("recognition_data/vehiclegame_v1_out_june14.csv") %>%
  as.tibble() %>%
  select(-X)

recog_data <- animal_game %>%
  full_join(vehicle_game)

## make copy for editing
orig_d  <- recog_data
d <- recog_data

# make similar levels
d$clicked_category = as.factor(d$clicked_category)
d$intended_category = factor(d$intended_category, levels=levels(d$clicked_category))

# compute accurcy
d <- d %>%
  mutate(correct_or_not = (clicked_category == intended_category))  

d$recognizer_age <- factor(d$recognizer_age, levels = c('age2','age3','age4','age5','age6','age7','age8','age9','age10','adult'))

c_vehicle <- read.csv("compiled_classifications/classification-outputs-vehiclegame_C_0.1_460.csv") %>%
  as.tibble() %>%
  select(-X.1, -X) %>%
  mutate(exp='vehiclegame')
  
  
## Import classifications
c <- read.csv("compiled_classifications/classification-outputs-animalgame_C_0.1_560.csv") %>%
  as.tibble() %>%
  mutate(exp='animalgame') %>%
  full_join(c_vehicle) %>%
  mutate(sketch_path = paste0(target_label,'_','sketch_age',age,'_cdm_',session_id)) %>%
  mutate(sketch_path = as.factor(sketch_path)) 
```

## Filter non-compliant subjects & trials
```{r}
adults <- d %>%
  filter(recognizer_age == 'adult')

didnt_start <- d %>%
  group_by(sessionId) %>%
  mutate(count_trials = max(trial_num)) %>%
  filter(count_trials < 5)

d <- d %>%
  filter(!sessionId %in% didnt_start$sessionId) %>%
  filter(!sessionId %in% adults$sessionId) %>%
  filter(RT>100 & RT<10000) # super long or super short trial

# ok_response_RT <- d %>%
#   filter(RT>100 & RT<10000) # super long or super short trial
# # calculate percent trials included
# percent_trials_included = length(ok_response_RT$RT) / length(d$RT)

```

```{r}
photo_correct <- d %>%
  group_by(sessionId,recognizer_age) %>%
  filter(producer_age == "photo") %>%
  summarize(avg_photo_correct = mean(correct_or_not)) 

threshold=.75
ggplot(photo_correct, aes(x=recognizer_age, y=avg_photo_correct, col=recognizer_age)) +
  geom_jitter(alpha=.6) +
  scale_color_viridis(discrete=TRUE) +
  geom_hline(yintercept=threshold)

bad_subs <- photo_correct %>%
  filter(avg_photo_correct < threshold)
```

## Filter out subs who don't meet photo correct threshold
```{r}
# filter bad subs
d <- d %>%
  filter(!sessionId %in% bad_subs$sessionId)

#check
photo_trials_by_sub <- d %>%
  filter(producer_age == 'photo') %>%
  group_by(sessionId) %>%
  summarize(avg_correct = mean(correct_or_not))

```

### Calculate number of trials per kid (not adult) after these exclusions
```{r}
num_trials_per_kid <- d %>%
  filter(!sessionId %in% adults$sessionId) %>% # exclude adults
  group_by(sessionId) %>%
  summarize(max_trials = max(trial_num)) %>%
  summarize(average_trials = mean(max_trials))
##
```

First, we excluded children who started the game but did not complete more than 1 trial after the practice trials (N = `r length(unique(didnt_start$sessionId))` participants) and the `r length(unique(adults$sessionId))` who participated. We also excluded all trials with RTs slower than 10s or faster than 100ms, judging these to be off-task responses. Next, we excluded participants on the basis of their performance on practice and catch trials; given that these catch trials presented a very easy recognition task, we excluded participants who did not acheive 80\% accuracy on these trials (N= `r length(bad_subs$sessionId)`). The remaining `r length(unique(d$sessionId))` who met this criterion completed an average of `r round(mean(num_trials_per_kid$average_trials),2)` trials. 

### Exclusion rates in each age bin; mostly filtering out young kids not on task.
```{r}
bad_subs_descriptives <- orig_d %>%
  filter(sessionId %in% bad_subs$sessionId) %>%
  group_by(sessionId) %>%
  summarize(count_trials = n(), recognizer_age = recognizer_age[1]) %>%
  group_by(recognizer_age) %>%
  summarize(count_subs = n(), avg_trials = mean(count_trials))

kable(bad_subs_descriptives)
```
### Number of subs left in each age 
```{r}
d %>%
  group_by(recognizer_age) %>%
  summarize(num_subs = length(unique(sessionId))) %>%
  kable()
```
### Number of subs left in each age group
```{r}
## filter recognition data to just kids and wrangle variables
kids_sketches_d <- d %>%
  filter(producer_age != 'photo') %>% # don't look at photo trials
  filter(recognizer_age != 'adult') %>%  # or adults
  filter(recognizer_age != 'age2') %>%  # or 2-yr-olds
  ## wrangle sketch paths so can be joined with classification data
  mutate(sketch_path = as.factor(str_split_fixed(sketch_path,'/',2)[,2])) %>% 
  mutate(sketch_path = as.factor(str_split_fixed(sketch_path,'.png',2)[,1])) %>% 
  mutate(recognizer_age_numeric = as.numeric(str_split_fixed(recognizer_age,'age',2)[,2])) %>% 
  mutate(recognizer_age_group = cut(recognizer_age_numeric, c(2.9, 5, 7, 9, 10.1), labels = c("3-4 yrs","5-6 yrs","7-8 yrs","9-10 yrs"))) %>%
  mutate(recognizer_age_group_numeric = cut(recognizer_age_numeric, c(2.9, 5, 7, 9, 10.1), labels=c(3,5,7,9))) %>%
  mutate(recognizer_age_group_numeric = as.numeric(recognizer_age_group_numeric))

kids_sketches_d %>%
  group_by(recognizer_age_group) %>%
  summarize(num_subs = length(unique(sessionId))) %>%
  kable()

```

### Look at classifier confusions across age
```{r}
animals = c('bird','fish','rabbit','dog')
c_mod_anim <- c %>%
  filter(exp=='animalgame') %>%
  rowwise() %>%
  mutate(max_val = which.max(c(bird_prob, fish_prob, rabbit_prob, dog_prob))) %>%
  mutate(assigned_category = animals[max_val]) 

c_mod_anim$assigned_category = as.factor(c_mod_anim$assigned_category)
c_mod_anim$intended_category = as.factor(c_mod_anim$target_label)

```

```{r}
vehicles = c('boat','car','airplane','train')
c_mod_vehicle <- c %>%
  filter(exp=='vehiclegame') %>%
  rowwise() %>%
  mutate(max_val = which.max(c(boat_prob, car_prob, airplane_prob, train_prob))) %>%
  mutate(assigned_category = vehicles[max_val]) 

c_mod_vehicle$assigned_category = as.factor(c_mod_vehicle$assigned_category)
c_mod_vehicle$intended_category = as.factor(c_mod_vehicle$target_label)

```

```{r plotConfusions, fig.width=8, fig.height=2}
confusions <- c_mod_vehicle %>%
  group_by(intended_category, assigned_category,age)  %>%
  summarize(number = n()) %>%
  group_by(intended_category) %>%
  mutate(prop = number / sum(number))

ggplot(confusions, aes(x=assigned_category, y=intended_category, fill=prop)) +
  geom_tile() + 
  scale_fill_gradient(limits = c(0, 1)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) + 
  ylab("Intended Category") + 
  xlab("Assigned Category") +
  scale_fill_viridis(option='A') + 
  facet_grid(~age) +
  theme_few()

```


## Examine recognition data by producer age, recognizer age, and interactions
### Compile averages to look at average correct
```{r plot-counts}
# summarize avg correct by producer age  
by_producer <- d %>%
  filter(recognizer_age!= 'adult') %>%
  group_by(producer_age) %>%
  multi_boot_standard(col = 'correct_or_not')

by_recognizer <- d %>%
  group_by(recognizer_age) %>%
  filter(producer_age != 'photo') %>%
  multi_boot_standard(col = 'correct_or_not')

by_recognizer_photo <- d %>%
  group_by(recognizer_age) %>%
  filter(producer_age == 'photo') %>%
  multi_boot_standard(col = 'correct_or_not') 

by_recognizer_dont_know <- d %>%
  mutate(dont_know = (clicked_category == 'dont_know')) %>%
  group_by(recognizer_age) %>%
  multi_boot_standard(col = 'dont_know') 
```


### Look at overall recognition by recognizer age -- whelp, 2-year-olds are getting help!
```{r}
by_recognizer$recognizer_age <- factor(by_recognizer$recognizer_age, levels = c('age2','age3','age4','age5','age6','age7','age8','age9','age10','adult'))

ggplot(by_recognizer,aes(x=recognizer_age, y=mean, col = recognizer_age)) +
  theme_few() +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  scale_color_viridis(discrete = "TRUE") + 
  ylab('Proportion drawings recognized') +
  ylim(.25,.8) +
  geom_smooth() 
  
```

### Look at use of "don't know" buton across age
```{r}
ggplot(by_recognizer_dont_know,aes(x=recognizer_age, y=mean, col = recognizer_age)) +
  theme_few() +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  scale_color_viridis(discrete = "TRUE") + 
  ylab('Proportion trials selected "dont know"') +
  geom_smooth() 
  
```



### How are recognizers in this group doing on photo trials?
```{r}
by_recognizer_photo$recognizer_age <- factor(by_recognizer_photo$recognizer_age, levels = c('age2','age3','age4','age5','age6','age7','age8','age9','age10','adult'))

ggplot(by_recognizer_photo,aes(x=recognizer_age, y=mean, col = recognizer_age)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  scale_color_viridis(discrete = "TRUE") + 
  ylab('Proportion recognized - PHOTO') +
  theme_few()
```
### Any correlation between photo-correct and overall correct?
```{r}
cor_by_trial_type <- d %>%
  mutate(photo_or_not = (producer_age == 'photo')) %>%
  group_by(photo_or_not,sessionId) %>%
  summarize(count_cor = sum(correct_or_not), count_items = n(), avg_correct = count_cor / count_items)

only_one_type <- cor_by_trial_type %>%
  group_by(sessionId) %>%
  summarize(count_ids = n()) %>%
  filter(count_ids == 1)

cor_by_trial_type <- cor_by_trial_type %>%
  filter(!sessionId %in% only_one_type$sessionId) 

cor.test(cor_by_trial_type$avg_correct[cor_by_trial_type$photo_or_not==TRUE], cor_by_trial_type$avg_correct[cor_by_trial_type$photo_or_not==FALSE])

qplot(cor_by_trial_type$avg_correct[cor_by_trial_type$photo_or_not==TRUE], cor_by_trial_type$avg_correct[cor_by_trial_type$photo_or_not==FALSE])

```

### By producer age ONLY, collapsing across recognizer age
```{r}
ggplot(by_producer,aes(x=producer_age, y=mean, col = producer_age)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  scale_color_viridis(discrete = "TRUE") + 
  ylab('Proportion recognized') +
  theme_few()
```

### How does this trend break down by each category?
```{r}
both_category <- d %>%
  group_by(producer_age,intended_category) %>%
  # filter(recognizer_age == "adult") %>%
  multi_boot_standard(col = 'correct_or_not') 

ggplot(both_category,aes(x=producer_age, y=mean, col=producer_age)) +
  theme_few() + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ylab('average correct') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), aspect.ratio = 1) +
  facet_wrap(~intended_category) +
  scale_color_viridis(discrete=TRUE) 

```

### Big item effects -- bird/dog are not gettting classified as well as fish/rabbit, much larger error bars than in actual recognition....
```{r}
cor_by_age <- c %>%
  group_by(age,target_label) %>%
  multi_boot_standard(col = 'correct_or_not') 

ggplot(cor_by_age, aes(x=age, y=mean, col=age)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  facet_wrap(~target_label) +
  theme_few() +
  theme(aspect.ratio = 1) +
  ylab('average classification accuracy') + 
  xlab('producer age') + 
  scale_color_viridis(discrete=FALSE)

```

### Now looking at producer x recognizer age
```{r}
both <- d %>%
  group_by(recognizer_age,producer_age) %>%
  multi_boot_standard(col = 'correct_or_not') 

levels(both$recognizer_age) = c('2 yrs','3 yrs','4 yrs','5 yrs','6 yrs','7 yrs','8 yrs','9 yrs','10 yrs','adult')
levels(both$producer_age) = c('4 yrs','5 yrs','6 yrs','7 yrs','8 yrs','photo')

(descriptives <- ggplot(both,aes(x=producer_age, y=mean, col=producer_age)) +
  theme_few(base_size=14) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ylab('Proportion recognized') +
  xlab('Age of drawer') + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1), aspect.ratio = 1, legend.position='none') +
  # facet_wrap(~recognizer_age, scales='free_x') +
    facet_wrap(~recognizer_age) +
  scale_color_viridis(discrete=TRUE))

# ggsave('mainResults.pdf', descriptives, width=6, height=8, dpi=300)
```

### Switch recognizer/producer age to re-visualize data
```{r}
both_plot <- both %>%
  group_by(recognizer_age)

ggplot(both_plot,aes(x=recognizer_age, y=mean, col=producer_age)) +
  theme_few() + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_smooth(method='lm') +
  ylab('average correct') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), aspect.ratio = 1) +
  facet_grid(~producer_age) +
  scale_color_viridis(discrete=TRUE) 
  

```


# Distinctiveness x Age analyses
## Compute distincitveness bins, join classifications & recognition data
```{r}
num_bins=10
## compute bins for distinctiveness
sketch_by_distinctiveness <- c %>%
  # filter(correct_or_not==1) %>%
  group_by(target_label) %>%
  mutate(distinct_index = ntile(target_label_prob,num_bins)) %>%
  select(sketch_path, distinct_index, target_label_prob)

##
sketch_by_distinctiveness_high_low <- c %>%
  mutate(distinct_index_highvlow = ntile(target_label_prob,2)) %>%
  select(sketch_path, distinct_index_highvlow)

## join distinctiveness bins for each sketch in dataset
all_joined <- kids_sketches_d %>%
  left_join(sketch_by_distinctiveness) %>%
  left_join(sketch_by_distinctiveness_high_low)
```

## For correctly classified ONLY : compute distincitveness bins, join classifications & recognition data
```{r}
sketch_by_distinctiveness_cor_only <- c %>%
  filter(correct_or_not==1) %>%
  group_by(target_label) %>%
  mutate(distinct_index = ntile(target_label_prob,num_bins)) %>%
  select(sketch_path, distinct_index, target_label_prob)

all_joined_classifier_cor_only <- kids_sketches_d %>%
  left_join(sketch_by_distinctiveness_cor_only) 
```

## How does distinctiveness bin vary with classifier probability /correctness?
```{r}
ggplot(sketch_by_distinctiveness, aes(x=distinct_index, y=target_label_prob)) +
  geom_point(alpha=.5) +
  facet_wrap(~target_label) +
  theme_few()

```



### Plot distinctivenss by age interaction, only using "don't know"
```{r fig.width=8, fig.height=2}
distinct_by_age_dont_know <- all_joined %>%
  mutate(dont_know = (clicked_category == 'dont_know')) %>%
  group_by(distinct_index, recognizer_age_numeric) %>%
  multi_boot_standard(col='dont_know') %>%
  group_by(distinct_index)

ggplot(distinct_by_age_dont_know, aes(x=distinct_index, y=mean, col=recognizer_age_numeric)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_smooth(alpha=.2, span=10, method='lm') +
  facet_grid(~recognizer_age_numeric) +
  theme_few() +
  scale_color_viridis(discrete=FALSE)
```


### Plot distinctivenss by item interaction
```{r fig.width=8, fig.height=2}
distinct_by_age <- all_joined %>%
  group_by(intended_category, distinct_index) %>%
  multi_boot_standard(col='correct_or_not') %>%
  group_by(distinct_index)

ggplot(distinct_by_age, aes(x=distinct_index, y=mean, col=intended_category)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_smooth(alpha=.2, span=10, method='lm') +
  facet_grid(~intended_category) +
  theme_few() 
```

### Plot distinctivenss by age interaction
```{r fig.width=8, fig.height=2}
distinct_by_age <- all_joined %>%
  group_by(recognizer_age_numeric, distinct_index) %>%
  multi_boot_standard(col='correct_or_not') %>%
  group_by(distinct_index)

ggplot(distinct_by_age, aes(x=distinct_index, y=mean, col=recognizer_age_numeric)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_smooth(alpha=.2, span=10) +
  facet_grid(~recognizer_age_numeric) +
  theme_few() + 
  scale_color_viridis(discrete=FALSE)
```


### Plot distinctivenss by age group interaction
```{r}
distinct_by_age <- all_joined %>%
  group_by(recognizer_age_group, distinct_index) %>%
  multi_boot_standard(col='correct_or_not') %>%
  group_by(distinct_index)

(distinct_by_age_plot <- ggplot(distinct_by_age, aes(x=distinct_index, y=mean, col=recognizer_age_group)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_smooth(alpha=.2, span=4, method='lm') +
  facet_grid(~recognizer_age_group) +
  theme_few(base_size = 22) + 
  scale_x_continuous(breaks=seq(1,10,2)) +
  xlab('Distinctiveness Index') +
  ylab('Proportion recognized') +
  theme(legend.position='none') + 
  scale_color_viridis(discrete=TRUE)) 

# ggsave('DistinctByAge.svg',distinct_by_age_plot, width=11)
```



### Plot distinctivenss by age group interaction for correctly classified drawings only
```{r}
distinct_by_age_cor_only <- all_joined_classifier_cor_only %>%
  group_by(recognizer_age_group, distinct_index) %>%
  multi_boot_standard(col='correct_or_not') %>%
  group_by(distinct_index)

(distinct_by_age_plot_cor_only <- ggplot(distinct_by_age_cor_only, aes(x=distinct_index, y=mean, col=recognizer_age_group)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_smooth(alpha=.2, span=4, method='lm') +
  facet_grid(~recognizer_age_group) +
  theme_few(base_size = 22) + 
  scale_x_continuous(breaks=seq(1,10,2)) +
  xlab('Distinctiveness Index') +
  ylab('Proportion recognized') +
  theme(legend.position='none') + 
  scale_color_viridis(discrete=TRUE)) 

# ggsave('DistinctByAge.svg',distinct_by_age_plot, width=11)
```

### Explore how distinctivenss vs age group interact in glmer 
```{r}
model_glmer <- glmer(correct_or_not ~ scale(distinct_index)*scale(recognizer_age_group_numeric) + (1|intended_category) + (1|sessionId),  data = all_joined, family='binomial')
summary(model_glmer)
```

```{r}
model_glmer_age_cont <- glmer(correct_or_not ~ scale(distinct_index)*scale(recognizer_age_numeric) + (distinct_index|intended_category) + (1|sessionId),  data = all_joined, family='binomial')
summary(model_glmer_age_cont)

```

