---
title: "Drawing-Recognition-Manuscript"
author: ""
date: "5/8/2019, updated 10/2020"
output: 
  html_document:
    toc: true
    theme: cerulean
---

# Preprocessing
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(ggplot2)
library(assertthat)
library(langcog)
library(viridis)
library(ggthemes)
library(lme4)
library(lmerTest)

```

# Load data
## Preprocessed recognition data
```{R}
load(file = here::here('data/recognition_data/recognition_data_preprocessed_without_vgg.RData'))

```

## CLIP classification data
```{R}
load(file = here::here('data/clip_outputs/fullset/clip_long.RData'))
```

```{r}
clip_to_merge <- clip_long %>%
  rename(producer_age_numeric = kid_age) %>%
  mutate(session_id = paste0("cdm_", session_id)) %>%
  mutate(category = str_replace(category,' ','.')) %>%
  mutate(sketch_path = paste0(category,'_sketch_age',producer_age_numeric,'_',session_id)) %>%
  filter(category == guessed_category) %>%
  rename(clip_prob = prob) %>%
  select(sketch_path, clip_prob)
```


```{R}
# all_meta <- read_csv(file = here::here('data/drawings/stringent_cleaned_dataset_meta/all_object_metadata_cleaned.csv')) %>%
#   as_tibble() %>%
#   mutate(category = str_split_fixed(category,' ',2)[,2]) %>%
#   mutate(category = str_replace(category,' ','.'))  # ice cream
# 
# test <- all_meta %>%
#   filter(category=='fish', age == 'age7', session_id == 'cdm_run_v21525455905420')
```

## Join datasets
```{r}
recog_by_clip <- kids_sketches_d %>%
  left_join(clip_to_merge, by=c('sketch_path')) %>%
  rename(log_odds = clip_prob) %>%
  filter(!is.na(log_odds))
```

## Some sketches (271) appeared in recoggames but not in big filtered dataset 
Super frustrating. Probaly errors in filtering/manual selection process.
Some sketches from early CDM runs (manually filtered)

```{r}
sketch_mismatch <- kids_sketches_d %>%
  filter(!sketch_path %in% clip_to_merge$sketch_path) %>%
  distinct(sketch_path, intended_category) %>%
  group_by(intended_category) %>%
  summarize(num_sketches = length(unique(sketch_path)))
```

```{R}
# fish_sketch_age7_cdm_run_v21525455905420

# what <- clip_long %>%
#   filter(category=='fish', kid_age == 7, session_id == 'run_v21525455905420')
```

```{r}

# assert_that(sum(is.na(recog_by_clip$log_odds))==0)
# 
# assert_that(length(unique(kids_sketches_d$sketch_path))==length(unique(recog_by_clip$sketch_path)))

```


```{r}
# what <- recog_by_clip %>%
#   filter(is.na(clip_prob)) %>%
#   select(sketch_path) %>%
#   distinct(sketch_path) %>%
#   filter(!sketch_path %in% clip_to_merge$sketch_path)


```


## Compute distincitveness bins (used for visualizations) join classifications & recognition data
```{r}
num_bins=10

## compute bins for distinctiveness
sketch_by_distinctiveness <- clip_to_merge %>%
  mutate(distinct_index = ntile(clip_prob,num_bins)) %>% ## compute bins based on log odds over entire dataset
  select(sketch_path, distinct_index, clip_prob)

## join distinctiveness bins for each sketch in dataset
all_joined <- kids_sketches_d %>%
  left_join(sketch_by_distinctiveness) %>%
  filter(!is.na(clip_prob))
```

## How does distinctiveness bin vary with probilities?
```{r}
ggplot(all_joined, aes(x=distinct_index, y=clip_prob)) +
  geom_jitter(alpha=.03) +
  facet_wrap(~intended_category) +
  theme_few()
```


### Plot distinctivenss by age interaction
```{r}
## Panel B in ms figure
distinct_by_age <- all_joined %>%
  group_by(recognizer_age_numeric, distinct_index) %>%
  multi_boot_standard(col='correct_or_not') %>%
  group_by(distinct_index) %>%
  mutate(recognizer_age_name = paste0(as.character(recognizer_age_numeric), '-year-olds'))
```


```{R}
 ggplot(distinct_by_age, aes(x=distinct_index, y=mean, col=as.factor(recognizer_age_numeric))) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha=.8, size=.2) +
  geom_smooth(alpha=.1, span=4, size=.5, method = 'lm') +
  # facet_wrap(~recognizer_age_numeric, nrow=2) +
  theme_few(base_size = 10) + 
  xlab('Classifier evidence') +
  ylab('Proportion drawings recognized') +
  theme(legend.position='none') + 
  scale_color_viridis(discrete=TRUE) +
  scale_x_continuous(
    breaks=c(2,9),
    labels=c(' Low ',' High ')
        ) +
  theme(axis.ticks.x=element_blank(), aspect.ratio=1) +
  geom_hline(yintercept=.25, linetype='dashed',color='grey') +
  ylim(0,1)
  

ggsave('figures/CLIP_distinctByAge.pdf', height=3, width=3, units='in')
```

```{r}
model_glmer <- glmer(correct_or_not ~ scale(clip_prob)*scale(recognizer_age_numeric) + (scale(clip_prob)|intended_category) + (1|sessionId),  data = all_joined, family='binomial')
out = summary(model_glmer)

round(out$coefficients,3)
xtable::xtable(summary(out)$coef, digits=3, caption = "Model coefficients of a GLMM predicting visual recognition performance as a function of recognizer age and visual 'distinctiveness' metrics (here, cross-modal CLIP probability,see Methods")

```



# Production vs. Recognition

### Computer recogniiton x age x category 
```{r}
recognizer_by_age_by_category <- all_joined %>%
  group_by(intended_category, recognizer_age_numeric) %>%
  summarize(avg_recognized = mean(correct_or_not), count = length(unique(sketch_path)))
```

```{r}
recognizer_by_age_by_category_high_acc <- all_joined %>%
  group_by(intended_category) %>%
  filter(clip_prob > quantile(clip_prob,.5, na.rm=TRUE)) %>%
  group_by(intended_category, recognizer_age_numeric) %>%
  summarize(avg_recognized = mean(correct_or_not), count = length(unique(sketch_path)))


recognizer_by_category_high_acc <- all_joined %>%
  group_by(intended_category) %>%
  filter(clip_prob > quantile(clip_prob,.75, na.rm=TRUE)) %>%
  group_by(intended_category,recognizer_age_numeric) %>%
  summarize(avg_recognized = mean(correct_or_not), count = length(unique(sketch_path)))
```

```{r}
load(here::here('data/clip_outputs/fullset/clip_by_image.RData'))
```

```{R}
clip_producer_age_by_category <- clip_by_image %>%
  mutate(sketch_path = paste0(category, '_sketch_','age', kid_age, '_cdm_', session_id)) %>%
 filter(!sketch_path %in% unique(all_joined$sketch_path)) %>%
  filter(category %in% unique(recognizer_by_age_by_category$intended_category)) %>%
  group_by(category, kid_age) %>%
  summarize(avg_recognized = mean(correct_or_not), count = length(unique(sketch_path)))  %>%
  mutate(mode = 'clip_recognition')
```

```{R}
both_clip <- recognizer_by_age_by_category_high_acc %>%
  rename(category = intended_category, age_numeric = recognizer_age_numeric) %>%
  mutate(mode = 'kid_recognition') %>%
  full_join(clip_producer_age_by_category %>% rename(age_numeric = kid_age)) %>%
  filter(!is.na(avg_recognized)) %>%
  pivot_wider(values_from = c(count, avg_recognized), names_from = c('mode')) %>%
  mutate(category = fct_drop(category)) %>%
  rename(kid = avg_recognized_kid_recognition, model = avg_recognized_clip_recognition ) %>%
  filter(!is.na(kid))


# clip_producer_age_by_category <- clip_by_image %>%
#   mutate(sketch_path = paste0(category, '_sketch_','age', kid_age, '_cdm_', session_id)) %>%
#   filter( !sketch_path %in% unique(all_joined$sketch_path)) %>%
#   filter(category %in% unique(recognizer_by_age_by_category$intended_category)) %>%
#   group_by(category, kid_age) %>%
#   summarize(avg_recognized = mean(correct_or_not), count = length(unique(sketch_path)))  %>%
#   mutate(mode = 'clip_recognition')
```


# Clip vs. kid recognition (wow, way better)

```{r}
ggplot(both_clip, aes(x=kid, y=model, col=category)) +
  geom_point(alpha=.8, aes(size=count_clip_recognition))  +
  # scale_color_viridis_c() +
  theme_few() +
  theme(aspect.ratio=1, legend.position = 'none')  +
  ylab('Production (Clip recognition)') +
  xlab('Recognition (Kid recognition)')  +
  scale_y_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1)) +
  scale_x_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1))   +
  geom_smooth(method='lm',alpha=.1, aes(weight=count_clip_recognition, group=age_numeric), color='grey') +
  ggrepel::geom_label_repel(aes(label = category), max.overlaps = 20, label.padding = .1, box.padding = .1, label.size = .5, alpha=.3) +
  facet_wrap(~age_numeric, nrow=2)
  
```


```{r}
ggplot(both_clip, aes(x=kid, y=model, col=category)) +
  geom_point(alpha=.8, aes(size=count_clip_recognition))  +
  # scale_color_viridis_c() +
  theme_few() +
  theme(aspect.ratio=1, legend.position = 'none')  +
  ylab('Production (Clip recognition)') +
  xlab('Recognition (Kid recognition)')  +
  scale_y_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1)) +
  scale_x_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1))   +
  geom_smooth(method='lm',alpha=.1, aes(weight=count_clip_recognition, group=age_numeric), color='grey') +
  ggrepel::geom_label_repel(aes(label = category), max.overlaps = 20, label.padding = .1, box.padding = .1, label.size = .5, alpha=.3) +
  facet_wrap(~age_numeric, nrow=2)
```
