---
title: "Photodraw2-Descriptives"
author: "Bria Long"
date: "2/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(assertthat)
```

## Import descriptives csv

```{r cars}
d <- read.csv("photodraw2_descriptives/MuseumStation_AllDescriptives_1619_images_final_CDM_photodraw_e2.csv") %>%
  as.tibble() %>%
  mutate(age_numeric =as.numeric(str_split_fixed(age,'age',2)[,2]))
```


## Check that we don't have duplicate subIDs -- whooops, we do!
```{r}
prac_trials = c('this square','this shape','triangle','rectangle')
double_sessions <- d %>%
  distinct(subID,session_id) %>%
  group_by(subID) %>%
  summarize(num_sessions = n()) %>%
  filter(num_sessions > 1)

drawings_by_doubles <-  d %>%
  filter(subID %in% double_sessions$subID) %>%
  filter(!category %in% prac_trials) %>%
  group_by(subID,category) %>%
  summarize(num_drawings = n()) %>%
  filter(num_drawings >1) 

```

### There is one subID that was used twice (two different ages and sessionIds). Fix it!
```{r}
duplicate_sub_id = unique(drawings_by_doubles$subID)
to_fix <- d %>%
  filter(subID == duplicate_sub_id) 

unique(to_fix$age) ## two ages here -- age 5 and 7 with the same subID

# To match run sheet: 111418_6 & age7 stays as ID 111418_6
# To match run sheet: 111418_6 & age5 should instead be 111418_5
assert_that(sum(d$session_id=="111418_5")==0) # isn't it the database yet, so that's the error

## FIX IT : change subid to character so can replace value; change back to factor to keep tidy
d <- d %>%
  mutate(subID = as.character(subID)) %>%
  mutate(subID=replace(subID, subID=="111418_6" & age=="age5","111418_5")) %>%
  mutate(subID = as.factor(subID))

```

## Filter any duplicate filenames just in case
```{r}
d <- unique(d)
```

### Check our CB by age counterbalancing
```{r cb-by-age}
cb_by_age<- d %>%
  group_by(age_numeric,CB) %>%
  distinct(subID) %>%
  summarize(num_participants = n()) 

kable(cb_by_age)
```


### Check that we have equal numbers of trials by condition/age
```{r cat-by-condition-by-age}

d %>%
  filter(!category %in% prac_trials) %>%
  group_by(condition,age_numeric) %>%
  summarize(num_drawings = n()) %>%
  kable()
```

## Look at counts by category
```{r plot-counts}
cat_by_cond_by_age<- d %>%
  group_by(age_numeric,condition,category) %>%
  summarize(num_drawings = n()) 

ggplot(cat_by_cond_by_age, aes(x = age_numeric, y = num_drawings, col=condition)) +
  geom_point() +
  facet_wrap(~category)
```


### Write out cleaned descriptives file
```{r}
d_out <- d %>%
  filter(age_numeric<9)  # get rid of 1 9-year-old for pilot recognition ratings

write_csv(d_out, 'photodraw2_descriptives/Photodraw2_SRCD_cleaned_data_4-8.csv')
```



```{r}
## Get randomized chunks for recognition batches

sample_set <- d %>%
  filter(age_numeric<9) %>%# get rid of 1 9-year-old for pilot recognition ratings
  filter(!category %in% prac_trials) %>% # no prac trials
  mutate(filename_short = str_split_fixed(filename,'/',10)[,10]) %>%
  distinct(subID,age_numeric,category,condition,filename_short,image_name) %>%
  rename(filename = filename_short)

##
max_iter=10

for (iteration in 1:max_iter) {

    if (iteration==max_iter){
      # whatever we have left if on last iteration
      write_csv(sample_set,paste0('recognition_rating_chunks/chunk_',iteration,'_photodraw2_srcd_recognition.csv'))
    }
    # for all the other iterations
    else if (iteration<max_iter){
  
    this_chunk <- sample_set %>%
      group_by(age_numeric,category) %>%
      sample_n(., 2, replace=FALSE)
    
    print (length(this_chunk$filename))
    write_csv(this_chunk,paste0('recognition_rating_chunks/chunk_',iteration,'photodraw2_srcd_recognition.csv'))
    
    sample_set <- sample_set %>%
      filter(!filename %in% this_chunk$filename)
    
    print (length(sample_set$filename))
    }
}

  

```