---
title: "Production_vs_recognition"
author: "Bria Long"
date: "6/20/2022"
output: html_document
---

# Libraries and data
```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(assertthat)
library(ggthemes)
library(egg)
library(viridis)
library(lme4)
library(lmerTest)
library(MuMIn)
library(langcog)
```

## Load metadata
```{r}
all_meta <- read_csv(file = here::here('data/drawings/stringent_cleaned_dataset_meta/all_object_metadata_cleaned.csv')) %>%
  as_tibble() %>%
  mutate(category = str_split_fixed(category,' ',2)[,2]) %>%
  mutate(category = str_replace(category,' ','.'))  # ice cream
```



## Load clip classification data
```{r}
load(file=here::here('data/clip_outputs/fullset/clip_by_image.RData'))
clip_by_image <-  clip_by_image %>%
  mutate(sketch_path = paste0(category, '_sketch_','age', kid_age, '_cdm_', session_id)) %>%
  rename(intended_category = category) %>%
  rename(producer_age_numeric = kid_age) %>%
  rename(clip_correct_or_not = correct_or_not) %>%
  rename(clip_prob = max_prob) %>%
  ungroup() %>%
  select(sketch_path, intended_category, producer_age_numeric,  clip_correct_or_not, clip_prob)

```

## Load recognition data (already joined with vgg classificationw)
```{r}
load(here::here('data/recognition_data/all_recognition_data_preprocessed.RData'))
recog_data = all_joined
rm(all_joined)
```

## Merge
```{r}
recog_data_by_both <- recog_data %>%
  mutate(producer_age_numeric = as.numeric(str_split_fixed(producer_age,'age',2)[,2])) %>%
  rename(vgg_correct_or_not = model_correct_or_not) %>%
  rename(vgg_log_odds = log_odds) %>%
  rename(vgg_distinct_index = distinct_index) %>%
  left_join(clip_by_image, by=c('sketch_path','intended_category', 'producer_age_numeric')) %>%
  filter(!is.na(clip_correct_or_not)) # don't have clip/vgg for every sketch -- some were filtered after inclusion in recoggames, 271 sketches

# mismatch <- recog_data_by_both %>%
  # filter(is.na(clip_correct_or_not))
  
  
```

# Choose which model

## Does clip or vgg do a better job of predicting kid recognition?
```{r}
by_image <- recog_data_by_both %>%
  group_by(sketch_path) %>%
  summarize(avg_kid_correct = mean(correct_or_not), clip_correct_or_not = mean(clip_correct_or_not), vgg_correct_or_not = mean(vgg_correct_or_not))


cor.test(by_image$avg_kid_correct, by_image$clip_correct_or_not)
cor.test(by_image$avg_kid_correct, by_image$vgg_correct_or_not)

diff = lm(data = by_image, avg_kid_correct ~ clip_correct_or_not*vgg_correct_or_not )
summary(diff)

```

```{r}
by_image_long <- by_image %>%
  pivot_longer(cols = clip_correct_or_not:vgg_correct_or_not, names_to='model', values_to = 'prop_recognized') %>%
  mutate(category = str_split_fixed(sketch_path,'_',2)[,1])

```

## Model vs. kid recognition by sketch
```{r}
ggplot(data = by_image_long, aes(x=prop_recognized, y=avg_kid_correct, color=model)) +
  geom_jitter(height=.1, alpha=.2) +
  geom_smooth(method='lm') + 
  facet_wrap(~category, nrow=4) +
  theme_few() +
  xlab('model recognition by sketch') +
  ylab('kid avg recognition by sketch')
```


## Create data structues


### By recognizer age

#### Compute recognititon x age x category  for top 30%
```{r}
recognizer_by_age_by_category <- recog_data_by_both %>%
  mutate(distinct_index_clip = ntile(clip_prob,10)) %>%
  filter(distinct_index_clip>7) %>%
  group_by(intended_category, recognizer_age_numeric) %>%
  summarize(avg_recognized = mean(correct_or_not), count = length(unique(sketch_path)))

# how well 3-year-olds recognized drawings of e.g., airplanes OF ALL AGES
```

## By producer age
###Compute averaged recognition x category/age by model
```{r}
clip_producer_age_by_category <- clip_by_image %>%
 filter(!sketch_path %in% unique(recog_data_by_both$sketch_path)) %>%
  filter(intended_category %in% unique(recog_data_by_both$intended_category)) %>%
  group_by(intended_category, producer_age_numeric) %>%
  summarize(avg_recognized = mean(clip_correct_or_not), count = length(unique(sketch_path)))  %>%
  mutate(mode = 'clip_recognition')
```


### Merge producer & recognizer age
```{r}
both_clip_long <- recognizer_by_age_by_category %>%
  rename(age_numeric = recognizer_age_numeric) %>%
  mutate(mode = 'kid_recognition') %>%
  full_join(clip_producer_age_by_category %>% rename(age_numeric = producer_age_numeric)) %>%
  filter(!is.na(avg_recognized))
  
both_clip <- both_clip_long %>%
  pivot_wider(values_from = c(count, avg_recognized), names_from = c('mode')) %>%
  mutate(category = fct_drop(intended_category)) %>%
  rename(kid = avg_recognized_kid_recognition, model = avg_recognized_clip_recognition ) %>%
  filter(!is.na(kid)) %>%
  mutate(drawings_total = count_kid_recognition + count_clip_recognition)


```

```{r}

## kid recognition: if a kid is 3-years-old, how many "airplane" drawings does he recognized on average
## kid production: if a kid is 3-year-old, how many "recognizable" airplanes drawings can he produce (on average)
# 
# both_clip_long <- recognizer_by_age_by_category %>%
#   mutate(mode = 'kid_recognition') %>%
#   full_join(clip_producer_age_by_category %>% rename(age_numeric = producer_age_numeric)) %>%
#   filter(!is.na(avg_recognized))
```

```{r}
both_clip_longer <- recognizer_by_age_by_category %>%
  rename(kid_recognition = avg_recognized) %>%
  right_join(clip_producer_age_by_category %>% rename(model_recognition = avg_recognized) %>% select(-count, -mode)) %>%
  filter(producer_age_numeric > 2)
  
```


# Plot it
## Main plot: recognition by producton

```{r}
ggplot(both_clip, aes(x=kid, y=model, color=category)) +
  geom_point(alpha=.4)  +
  theme_few(base_size=10) +
  theme(aspect.ratio=1, legend.position = 'none')  +
  ylab('Production (CLIP recognition accuracy)') +
  xlab('Recognition (Children\'s recognition accuracy)')  +
  scale_y_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1)) +
  scale_x_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1))   +
  geom_smooth(method='lm',alpha=0, size=.5, aes(weight=count_clip_recognition, group=age_numeric), color="#555555") +
  ggrepel::geom_label_repel(aes(label = category), size=1.5, max.overlaps = 30, force_pull=3,  label.padding = .1, box.padding = .1, label.size = .1,  alpha=.8, segment.color = NA)  +
  facet_wrap(~age_numeric, nrow=2)

ggsave('figures/production_vs_recognition_v2.pdf', width=7.5, height=3, units='in')

```

```{r}
## Entire age matrix

# ggplot(both_clip_longer, aes(x=kid_recognition, y=model_recognition, col=intended_category)) +
#   geom_point(alpha=.8)  +
#   # scale_color_viridis_c() +
#   theme_few() +
#   theme(aspect.ratio=1, legend.position = 'none')  +
#   ylab('Production (Clip recognition)') +
#   xlab('Recognition (Kid recognition)')  +
#   scale_y_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1)) +
#   scale_x_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1))   +
#   geom_smooth(method='lm',alpha=.1, color='grey') +
#   ggrepel::geom_label_repel(aes(label = intended_category), max.overlaps = 100, label.padding = .2, box.padding = .2, label.size = 0,  alpha=.3,) +
#   facet_grid(recognizer_age_numeric~producer_age_numeric)

  
```



## Category heatmaps for producer by recognizer age

```{R}
producer_by_recognizer_age <- recog_data_by_both %>%
  group_by(producer_age_numeric, recognizer_age_numeric, intended_category) %>%
  summarize(avg_correct = mean(correct_or_not)) %>%
  group_by(intended_category) %>%
  mutate(avg_cat_correct = mean(avg_correct)) %>%
  ungroup() %>%
  mutate(intended_category = fct_reorder(intended_category,-avg_cat_correct, .desc=TRUE))
  
```

```{r}
ggplot(producer_by_recognizer_age, aes(x=intended_category, y=avg_correct, color=intended_category)) +
  geom_point(alpha=.5) +
  theme_few() +
  
  facet_grid(producer_age_numeric~recognizer_age_numeric) +
  geom_smooth(method='lm', alpha=.01)
  
```

```{r}
ggplot(data = producer_by_recognizer_age, aes(x=producer_age_numeric, y=recognizer_age_numeric,fill=avg_correct)) + 
  geom_tile() + 
  theme_few(base_size = 12) +
  theme(legend.position = 'bottom', axis.text.x = element_text(angle = 0,  
  size = 6, vjust=.5, hjust = 1), axis.text.y = element_text(angle = 0,
  size = 6, hjust = 1)) + 
  coord_fixed() + 
  scale_fill_viridis(option="A", name = 'Percent recognized')  +
  ylab('Recognizer age') +
  xlab('Producer age') +
  facet_wrap(~intended_category)
```


## Without age data, not really enoguh points to show?
```{r}
# no_age_clip <- both_clip %>%
#   group_by(category) %>%
#   summarize(avg_model = mean(model), avg_kid = mean(kid), count_kid_recognition = count_kid_recognition[1])
```

```{r}
# ggplot(no_age_clip, aes(x=avg_model, y=avg_kid, col=category)) +
#   geom_point(alpha=.8)  +
#   theme_few() +
#   theme(aspect.ratio=1, legend.position = 'none')  +
#   ylab('Production (CLIP recognition)') +
#   xlab('Recognition (Kid recognition)')  +
#   scale_y_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1)) +
#   scale_x_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1))   +
#   geom_smooth(method='lm',alpha=.8) +
#   ggrepel::geom_label_repel(aes(label=category), max.overlaps=20, size=2)
```


# Appendix




# Not included
# VGG
## Load vgg classification data
```{r}
load(file=here::here('data/compiled_classifications/vgg_outputs.RData'))
```

```{r}
producer_age_by_category <- all_layer_class %>%
  mutate(correct_or_not = as.numeric(as.logical(correct_or_not))) %>%
  filter(layer=='FC6') %>%
  mutate(sketch_path = as.factor(str_split_fixed(image_name,'.png',2)[,1])) %>%
  filter(!sketch_path %in% unique(recog_data$sketch_path)) %>%
  filter(category %in% unique(recognizer_by_age_by_category$intended_category)) %>%
  group_by(category, age_numeric) %>%
  summarize(avg_recognized = mean(correct_or_not), count = length(unique(sketch_path))) %>%
  mutate(mode = 'vgg_recognition')
```

### vgg averaged recognition x category by kids
```{r}
recognizer_by_age_by_category <- recog_data_by_both %>%
  filter(vgg_distinct_index>7) %>%
  group_by(intended_category, recognizer_age_numeric) %>%
  summarize(avg_recognized = mean(correct_or_not), count = length(unique(sketch_path)))

both <- recognizer_by_age_by_category %>%
  rename(category = intended_category, age_numeric = recognizer_age_numeric) %>%
  mutate(mode = 'kid_recognition') %>%
  full_join(producer_age_by_category) %>%
  filter(!is.na(avg_recognized)) %>%
  pivot_wider(values_from = c(count, avg_recognized), names_from = c('mode')) %>%
  mutate(category = fct_drop(category)) %>%
  rename(kid = avg_recognized_kid_recognition, model = avg_recognized_vgg_recognition ) %>%
  filter(!is.na(kid))
```


## VGG vs. kid recognition
```{r}
ggplot(both, aes(x=kid, y=model, col=category)) +
  geom_point(alpha=.8, aes(size=count_vgg_recognition))  +
  # scale_color_viridis_c() +
  theme_few() +
  theme(aspect.ratio=1, legend.position = 'none')  +
  ylab('Production (VGG recognition)') +
  xlab('Recognition (Kid recognition)')  +
  scale_y_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1)) +
  scale_x_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1))   +
  geom_smooth(method='lm',alpha=.1, aes(weight=count_vgg_recognition, group=age_numeric), color='grey') +
  ggrepel::geom_label_repel(aes(label = category), max.overlaps = 20, label.padding = .1, box.padding = .1, label.size = .5, alpha=.3) +
  facet_wrap(~age_numeric, nrow=2)

```



```{r}
# ggplot(both_clip, aes(x=kid, y=model, col=age_numeric)) +
#   geom_point(alpha=.8, aes(size=count_clip_recognition))  +
#   scale_color_viridis_c() +
#   theme_few() +
#   theme(aspect.ratio=1, legend.position = 'none')  +
#   ylab('Production (CLIP recognition)') +
#   xlab('Recognition (Kid recognition)')  +
#   scale_y_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1)) +
#   scale_x_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1))   +
#   geom_smooth(method='lm',alpha=.1, aes(weight=count_clip_recognition, group=age_numeric)) 
```








### age x category x dataset
```{R}
# devphotodraw_vs_recoggames <- devphotodraw_recog %>%
#   left_join(recognizer_by_age_by_category, by=c('category' = 'intended_category', 'age' = 'recognizer_age_numeric')) %>%
#   rename(recognition = avg_recognized, production = prop_correct) %>%
#   filter(!is.na(recognition))
```

```{r}
# ggplot(devphotodraw_vs_recoggames, aes(x=production, y=recognition, color=category)) +
#   geom_point() +
#   theme_few() +
#   # scale_color_viridis_c() +
#   # geom_smooth(method='lm', color='grey') +
#   ylab('Avg category recognition (recoggames)') +
#   xlab('Avg category production by age of producer (humans, devphotodraw)') +
#   facet_wrap(~age, nrow=2)

```


```{r}
# devphotodraw_vs_recoggames_by_category <- devphotodraw_vs_recoggames %>%
#   group_by(category) %>%
#   summarize(production = mean(production), recognition = mean(recognition))
```

``


```{r}
# both_clip_long <- both_clip %>%
#   pivot_longer(cols = c(kid,model), names_to='mode',values_to="prop_correct")

```

```{r}
# ggplot(both_clip_long, aes(x=age_numeric, y=prop_correct, col=mode)) +
#   geom_point(alpha=.8)  +
#   # scale_color_viridis_c() +
#   theme_few() +
#   theme(aspect.ratio=1, legend.position = 'none')  +
#   # ylab('Production (Clip recognition)') +
#   # xlab('Recognition (Kid recognition)')  +
#   scale_y_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1)) +
#   # scale_x_continuous(breaks=c(0,.2,.4,.6,.8, 1), limits=c(0,1))  +
#   # geom_smooth(method='lm',alpha=.1, color='grey') +
#   # ggrepel::geom_label_repel(aes(label = category), max.overlaps = 20, label.padding = .1, box.padding = .1, label.size = .5, alpha=.3) +
#   facet_wrap(~category)
  
```



```{r}
# permuted <- mtcars %>%
#   mutate(am = factor(am)) %>% # factor am
#   modelr::permute(n, am) %>% # permute the am column `n` times
#   mutate(models = map(perm, ~ cor(wt ~ am, data=.)))
```


```{r}
# for (iter in c(1:100)){
#   perm =  cor.test(both$kid, both$model[sample(length(both$kid))])
#   if (iter==1){
#     vals = perm$estimate
#   }
#   vals = append(vals, perm$estimate)
# }
```

```{r}
# both_shuffled <- both %>%
#   select(category, kid, model) %>%
#   modelr::permute(100, category, kid) %>%
#   mutate(models = map(perm, ~ cor(kid ~ model, data = .)))
#   # mutate(tidy = map(models, broom::glance)) %>% #
#   # unnest(tidy) # unnest the tidy column

```





