---
title: "3_examine_classification_outputs"
author: "Bria Long"
date: "11/20/2018"
output: 
  html_document:
    toc: true # make table of contents
    toc_depth: 3
    theme: united
    highlight: tango 
---

```{r setup, include=FALSE}
library(tidyverse)
library(readr)
library(assertthat)
library(knitr)
library(ggplot2)
library(ggthemes)
library(lme4)
library(stringr)
```

## Read in and clean up datafiles
### Read in classification outputs (from get_classifications.py)

```{r}
dist <- read.csv('distinct_csvs/a person_v_a bowl_by_age.csv') %>%
  mutate(image_name = paste(target_class_label,'_sketch_', 'age',age,'_', session_id,'.png',sep="")) %>%
  mutate(image_path = paste('srcd-features/museumstation_sketches/',target_class_label,'/',image_name,sep=""))
##
dist$distinctiveness_score = dist$dist_conf-dist$dist_target
thres = quantile(dist$distinctiveness_score,.01)

least_distinct <- dist %>%
  filter(distinctiveness_score < thres) 
  
least_distinct_dir='not_distinct_person_bowl'
dir.create(least_distinct_dir)
file.copy(least_distinct$image_path, least_distinct_dir)
  
# ggplot(dist, aes(age,dist_target)) +
#   theme_few() +
#   geom_jitter(alpha=.2, height=0, width=.2) +
#   geom_smooth() 

ggplot(dist, aes(age,dist_conf-dist_target)) +
  theme_few() +
  geom_jitter(alpha=.2, height=0, width=.2) +
  geom_smooth(method = "lm")
```


```{r}
dist <- read.csv('distinctiveness_try.csv')
ggplot(dist, aes(ages,distinctiveness)) +
  theme_few() + 
  geom_jitter(alpha=.2, height=0, width=.2) +
  geom_smooth() + 
  facet_wrap(~class_labels)
```

```{r}
meta <- read.csv('classification-outputs/museumstation_subset_classification.csv') %>%
  as.tibble() %>%
  mutate(session_id = paste('cdm_',session_ids,sep="")) %>%
  mutate(age_numeric = ages) %>%
  mutate(age = paste('age',ages,sep="")) %>%
  mutate(category = target_classes) %>% 
  mutate(category_short = str_split_fixed(category," ",2)[,2]) %>%
  mutate(image_name = paste(category,'_sketch_', age,'_', session_id,'.png',sep="")) %>%
  select(-X) 
```

### Render out best classified sketches
```{r}
upper_thres = quantile(meta$target_label_prob,.99, na.rm = TRUE)

best_classified <- meta %>%
  filter(target_label_prob > upper_thres) %>%
  mutate(image_path = paste('srcd-features/museumstation_sketches/',category,'/',image_name,sep=""))

high_classified_dir='scrd_subset_highly_classified'
dir.create(high_classified_dir)
file.copy(best_classified$image_path, high_classified_dir)

```
### Render out worst classified sketches
```{r}
lower_thres = quantile(meta$target_label_prob,.01, na.rm = TRUE)
worst_classified <- meta %>%
  filter(target_label_prob < lower_thres) %>%
  mutate(image_path = paste('srcd-features/museumstation_sketches/',category,'/',image_name,sep=""))

worst_classified_dir='scrd_subset_worst_classified'
dir.create(worst_classified_dir)
file.copy(worst_classified$image_path, worst_classified_dir)
```


### Merge with mongodb database outputs (stroke count, duration, etc.)
Now should be able to look at target label probabilties for each image as a function of all of these other factors
```{r}
mongodb_meta <- read.csv('mongodb-output/MuseumStation_AllDescriptives_20780_images_final_cdm_run_v3.csv') %>%
  as.tibble() %>%
  left_join(meta) %>% # should join on session_id, category, age -- combination of which is unique identifier for an image
  filter(!is.na(target_label_prob)) # if intermediate file, only look where we have data

# main variable with merged data
d<- mongodb_meta
```
## Basic plots 
### age x log_probability of target class
```{r}

ggplot(d, aes(age_numeric,log(target_label_prob), color=image_scores)) +
  geom_point(alpha=.5) +
  theme_few() + 
  geom_smooth() +
  facet_wrap(~category) +
  labs(x='Age', y='Log probability', color="correctly classified?")
```

### age x classification accuracy 
```{r}
ggplot(d, aes(age_numeric,image_scores)) +
  theme_few() + 
  geom_jitter(alpha=.2, height=0, width=.2) +
  geom_smooth() + 
  facet_wrap(~category)
```

### Num strokes x target_label_prob
```{r}
ggplot(d, aes(num_strokes,log(target_label_prob), color=image_scores)) +
  geom_point(alpha=.5) +
  theme_few() + 
  geom_smooth(method='lm') +
  facet_wrap(~category)
```

### Mean intensity x target_label_prob
```{r}
ggplot(d, aes(mean_intensity,log(target_label_prob), color=image_scores)) +
  geom_point(alpha=.5) +
  theme_few() + 
  geom_smooth(method='lm') +
  facet_wrap(~category)
```

### Draw duration x target_label_prob
```{r}
ggplot(d, aes(draw_duration_old,log(target_label_prob), color=image_scores, names = "recognized or not")) +
  geom_point(alpha=.5) +
  theme_few() + 
  geom_smooth(method='lm') +
  facet_wrap(~category) +
  labs(x='Time spent drawing', y='Log probability', color="correctly classified?")
```

## Inferential stats
### Generalized linear mixed models with all covariates 
```{r}
mod_covariates <- glmer(image_scores ~ scale(age_numeric) +
                          scale(draw_duration_old) +
                          scale(mean_intensity) +
                          scale(num_strokes) +
                        (1|session_id) +
                        (1|category),
      data = d,
      family = "binomial")
modelOut=summary(mod_covariates)
kable(summary(mod_covariates)$coef, digits = 3)
```

```{r}
mod_covariates <- lmer(log(target_label_prob) ~ scale(age_numeric) +
                          scale(draw_duration_old) +
                          scale(mean_intensity) +
                          scale(num_strokes) +
                        (1|session_id) +
                        (1|category),
      data = d)
modelOut=summary(mod_covariates)
kable(summary(mod_covariates)$coef, digits = 3)

```

### Generalized linear mixed model with all covariates *and their interactions*
``` {r}
# mod_covariates_age <- glmer(image_scores ~ (scale(age_numeric) + 
#                           scale(draw_duration_old) + 
#                           scale(num_strokes))^2 +
#                         (1|session_id), 
#       data = d,  
#       family = "binomial")
# kable(summary(mod_covariates_age)$coef, digits = 3)
```
