---
title: "PhotoDraw-Exp1-RecognitionAnalysis"
author: "Bria Long"
date: "8/6/2018"
output: html_document
---

```{r setup, echo = FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(lmerTest)
library(viridis)
theme_set(theme_few())
```

## Load data and do basic preprocessing.
```{r}
## Read in data outputs from turk data - true/false recognition 
r <- read.csv("preprocessed_data/photodraw_recognition_ratings.csv") %>%
  as.tibble() 

## refactor levels to that semantic condition is first, then working memory, then perception
r$condition <- factor(r$condition, levels = c("S", "W", "P"))

d <- read_csv("preprocessed_data/photodraw_data_Aug8.csv") %>%
  select(-X1) %>%
  filter(!is.na(age)) %>%
  mutate(imNameShort = paste0(category, '_sketch', '_', session_id,'_',condition, '_', age,'.png'))

```

#### Convert alphanumeric age to numeric age in python csv
```{r}
d <- d %>%
  group_by(session_id) %>%
  mutate(age_char = strsplit(age,"e")[[1]][2]) %>%
  mutate(age_num = as.numeric(age_char)) %>%
  select(-age) %>%
  rename(age = age_num)
```

#### Join ratings and python datasets
```{r}
joined <- left_join(r,d)
```

### Sanity check number of raters per image
```{r}
ratersPerImage <- r %>%
  distinct(imageName, workerid) %>%
  group_by(imageName) %>%
  summarize(count = n()) 

assert_that(sum(ratersPerImage$count==30)==(length(unique(r$imageName))))
```

#### Sanity check number of kids in each condition and age
```{r}
r %>%
  distinct(sessionId, condition, age) %>%
  group_by(condition) %>%
  summarize(count = n()) %>%
  kable()
```

#### And distribution across age groups and conditions
```{r}
r %>%
  distinct(sessionId, condition, age) %>%
  group_by(condition,age) %>%
  summarize(count = n()) 
```


# Part 2: Descriptive statistics 

### Take a look at the raw rating data 
Highest chosen category is correct one;  confusions look more or less reasonable.
```{r}
ratingConfusions <- r %>%
  group_by(category, rating)  %>%
  summarize(number = n()) %>%
  group_by(category) %>%
  mutate(prop = number / sum(number)) %>%
  complete(rating, fill = list(prop = 0))

ratingConfusions$category <- factor(ratingConfusions$category, levels = c("rabbit","cat", "cup","shoe","train"))

ratingConfusions$rating <- factor(ratingConfusions$rating, levels = c( "rabbit","cat", "cup","shoe","train","bus","car","couch","bird","mouse","dog","horse","bear","lion","arm","hat","book","bottle","spoon","lamp","other","cannot tell at all"))

ggplot(ratingConfusions, 
       aes(x = rating, y = category, fill = prop)) + 
  geom_tile() + 
  ylab("True Category") + 
  xlab("Rated as") + 
  scale_fill_viridis(limits = c(0, 0.6),option="viridis") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```


### Look at num strokes / duration per condition

```{r}
ggplot(d, aes(num_strokes)) +
  geom_histogram(binwidth=2) + 
  facet_grid(~condition)

ggplot(d, aes(draw_duration)) +
  geom_histogram(binwidth=2) + 
  facet_grid(~condition)

```



## How different are individual participants?
```{r}

## Get proportion recognized for each image
correctByImage <- r %>%
  group_by(imNameShort) %>% # group by subjects
  mutate(image_correct = mean(correct)) %>%
  distinct(sessionId, category, age, image_correct, condition)

## Get proportion recognized for each participant
indiv <- r %>%
  group_by(sessionId) %>%
  mutate(sub_correct = mean(correct)) %>%
  distinct(sessionId, sub_correct, age) %>% # get unique combos of sessionId and average 
  ungroup() %>%
  mutate(sessionId = fct_reorder(sessionId, sub_correct, .desc=TRUE))

  # indiv_plot <- indiv %>%
#   ungroup(sessionId) %>%
#   mutate(sessionId = fct_reorder(sessionId, sub_correct, .desc=TRUE))  # reorder subjects from best to worst

## Plot individual children
ggplot(indiv, aes(x = sessionId, y = sub_correct, col = age)) +
  geom_point() + 
  # theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  theme(axis.text.x = element_blank())+
  xlab("Individual children") +
  ylab("Proportion Recognized") +
  scale_color_viridis() +
  geom_hline(yintercept=1/22, col='grey') # plot chance line 
```


## look at cannot tell at all
```{r}

## Get proportion recognized for each image
canttellByImage <- r %>%
  mutate(canttell=(rating=="cannot tell at all")) %>%
  group_by(imNameShort) %>% # group by subjects
  mutate(image_canttell = mean(canttell)) %>%
  distinct(sessionId, category, age, image_canttell, condition)

## Get proportion recognized for each participant
indivCanttell <- r %>%
  mutate(canttell=(rating=="cannot tell at all")) %>%
  group_by(sessionId) %>%
  mutate(sub_canttell = mean(canttell)) %>%
  distinct(sessionId, sub_canttell, age) %>% # get unique combos of sessionId and average 
  ungroup() %>%
  mutate(sessionId = fct_reorder(sessionId, sub_canttell, .desc=TRUE))

  # indiv_plot <- indiv %>%
#   ungroup(sessionId) %>%
#   mutate(sessionId = fct_reorder(sessionId, sub_correct, .desc=TRUE))  # reorder subjects from best to worst

## Plot individual children
ggplot(indivCanttell, aes(x = sessionId, y = sub_canttell, col = age)) +
  geom_point() + 
  # theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  theme(axis.text.x = element_blank())+
  xlab("Individual children") +
  ylab("Proportion Recognized") +
  scale_color_viridis() +
  geom_hline(yintercept=1/22, col='grey') # plot chance line 
```



##  How does recognizability vary acrosscondition ?
```{r}
corbyConditionAndSubID <- r %>%
  mutate(canttell=(rating=="cannot tell at all")) %>%
  group_by(sessionId) %>%
  mutate(meanCanttell = mean(canttell)) %>%
  distinct(sessionId,meanCanttell,condition) %>% # get rid of duplicates
  group_by(condition) %>%
  multi_boot_standard(col = "meanCanttell")  

ggplot(corbyConditionAndSubID, aes(x = condition, y = mean, col=condition)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_x_discrete(labels=c("Semantic","Working Memory","Perception")) +
  ylab("Proportion Canttell")

```


```{r}

corbyConditionAndSubID <- r %>%
  group_by(sessionId) %>%
  mutate(meanCorrect = mean(correct)) %>%
  distinct(sessionId,meanCorrect,condition) %>% # get rid of duplicates
  group_by(condition) %>%
  multi_boot_standard(col = "meanCorrect")  

ggplot(corbyConditionAndSubID, aes(x = condition, y = mean, col=condition)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_x_discrete(labels=c("Semantic","Working Memory","Perception")) +
  ylab("Proportion Recognized")
```


### Look at individual children's performance in these conditions by their age
```{r}
corbyChild <- r %>%
  group_by(condition,sessionId, age) %>%
  mutate(avgCorrect = mean(correct)) 

ggplot(corbyChild, aes(x = age, y = avgCorrect, col=age)) + 
  geom_jitter(width = .01, alpha = .5)  +
  facet_grid(~condition) + 
  scale_color_viridis() +
  ylab("Proportion Recognized")
```

##  How does recognizability vary across age and condition, collapsing across items?
```{r}
## Get the percent recognized for each age group / condition
corbyCondition <- r %>%
  group_by(sessionId, age, condition) %>% # group by subjects
  summarise(meanCorrect=mean(correct)) %>% # calculate mean correct (subject-level average correct)
  group_by(condition,age) %>% ## critical step: group by BOTH condition and age to get CIs for each combination of age (4,5,6,7) and condition (S,W,P)
  multi_boot_standard(col = "meanCorrect")  

ggplot(corbyCondition, aes(x = age, y = mean, col=age)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  facet_grid(~condition)+
  scale_color_viridis() +
  xlab("Children's Age") +
  ylab("Proportion Recognized")+
  scale_y_continuous(limits=c(-0.1,1))
```


```{r}

```



## At the image level,how do num strokes / draw duration / avg_stroke_legth relate to recognizability?
```{r} 
corByItem <- joined %>%
  group_by(imNameShort) %>%
  mutate(avgCorrect = mean(correct)) %>% # IMAGE level correctness
  distinct(imNameShort, avgCorrect, draw_duration, num_strokes, avg_stroke_length,age, condition)
```

```{r}
ggplot(corByItem, aes(x = num_strokes, y = avgCorrect, col=condition)) +
    geom_jitter(width = .1, alpha = .5) +
    facet_grid(~age)

ggplot(corByItem, aes(x = draw_duration, y = avgCorrect, col=condition)) +
    geom_jitter(width = .1, alpha = .5) +
    facet_grid(~age)
```

## How does this trend break down by the catergory that children drew?
```{r}
ggplot(correctByImage, aes(x = condition, y = image_correct, col=age)) + 
  geom_point() +
  facet_wrap(~category) + 
  scale_color_viridis() 

ggplot(correctByImage, aes(x = condition, y = image_correct, col=age)) + 
  geom_jitter() +
  facet_wrap(~category) 
```

# Part 3: Inferential Statistics

## Inferential analyses: Non-linear mixed effect model with random slopes for items and random intercepts for participants. 
```{r}
corbySketch <- r %>%
  group_by(imNameShort) %>%
  mutate(propCorrect=mean(correct)) %>%
  distinct(imNameShort, condition, age, category, propCorrect, sessionId) 

# scale age
corbySketch$age_sc = scale(corbySketch$age, scale = FALSE) # center but don't scale age

## Adding random slopes on participants causes the model to fail to converge, only keeping random intercepts.
model_lmer <- lmer(propCorrect ~ age_sc*condition + (1 | sessionId) + (condition | category),  data = corbySketch)

model_summary = summary(model_lmer)
```
### Check residuals of the model

Seem relatively evenly distributed around zero; suggests lmer isn't too bad of a fit.
```{r}
plot(corbySketch$age,resid(model_lmer))
plot(corbySketch$condition,resid(model_lmer))
```

### Get out some model predictions and plot them on top of both the raw data for each sketch and at the participant-averaged level

```{r}
predicted_df = data.frame(lmer_predictions = predict(model_lmer, corbySketch), age=corbySketch$age, condition=corbySketch$condition)

## Model prediction lines overlaid on raw data fed to the model
ggplot(data = predicted_df, aes(x=age, y=lmer_predictions)) +
  facet_grid(~condition) +
  scale_color_viridis()  +
  stat_smooth(method="lm", col='grey') + # plot smoothed line over predictions
  scale_x_discrete(limits=c(4,5,6,7),labels=c("4 yrs", "5 yrs", "6 yrs", "7 yrs")) +
  geom_jitter(data = corbySketch, aes(x=age, y=propCorrect, col=age)) # now plot raw corbysketch data

## Model prediction lines overlaid on subject-level CI data
corbyCondition<-corbyCondition %>%
  mutate(Age = age)

corbyCondition$Age=as.factor(corbyCondition$Age)

ggplot(data = predicted_df, aes(x=age, y=lmer_predictions)) +
  facet_grid(~condition) +
  stat_smooth(method="lm", col='grey') + # plot smoothed line
  geom_pointrange(data = corbyCondition,aes(x = age, y = mean, col=Age, ymin = ci_lower, ymax = ci_upper)) + # now remake same plot from before with 95% CIs
  xlab("Children's Age") +
  ylab("Proportion Recognized")+
  scale_y_continuous(limits=c(-0.1,1))+
  scale_color_viridis(discrete = TRUE)  

```

## Exploratory analysis: We have a somewhat uneven distribution of kids across ages (though even across condition). Do these results hold when we bin by "younger" and "older" kids to get a more even split?

### Plot how accuracy differs by these age group and condition
```{r}
r <- r %>%
  mutate(age_group = cut(age, c(3.9, 5, 8), labels = c("4-5","6-7"))) 

corbyAgeGroup <- r %>%
  group_by(sessionId)%>%
  mutate(meanCorrect = mean (correct)) %>%
  distinct(sessionId, age_group, condition, meanCorrect)%>%
  group_by(condition, age_group) %>%
  multi_boot_standard(col="meanCorrect")

ggplot(corbyAgeGroup, aes(x = condition, y = mean, col=age_group)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper))
```

### Run inferential model statistics for age group
```{r}
corbySketch <- corbySketch %>%
  mutate(age_group = cut(age, c(3.9, 5, 8), labels = c("4-5","6-7"))) 

model_lmer <- lmer(propCorrect ~ age_group*condition + (1 | sessionId) + (condition | category),  data = corbySketch)
summary(model_lmer)
```

Looks like we still see an interaction between age_group and condition, though the main effect of 4-5 year-olds and 6-7 year-olds is no longer significant on it's own.


SRCD Abstract:

The role of memory in children’s drawings of object categories
Bria Long, Judy Fan, Yi Feng, Renata Chai, & Michael C. Frank

Children’s drawings of object categories (e.g., rabbit, cat) become more and more recognizable as they get older, including visual features that distinguish these categories from one another (Long, Fan, & Frank, 2018). Why might older children tend to include these kinds of features (e.g., longer ears when drawing a rabbit)? One possibility is that younger children have a harder time accessing and retrieving their visual representations of what things tend to look like. Here, we examined whether children would draw more recognizable versions of objects when they heard a verbal cue accompanied by a picture of a canonical exemplar of this category (e.g., “can you draw a rabbit?”; working memory condition) and when they were asked to draw from perception (e.g., “can you draw this rabbit in the picture”) versus when they only heard a verbal cue (semantic condition).

Children ages 4-7 years (N = 60 total; 20 children in each condition) participated in a quick drawing game designed to test this hypothesis and were randomly assigned to one of these three conditions and drew five object categories (cup, shoe, rabbit, cat, train). The recognizability of children’s drawings was then assessed via adult raters (N = 30 per image, N = 90 total) who completed a 22AFC task with identity of each object category; drawings were only counted as recognizable if the adult rater guessed the correct category. These recognition scores for each drawing were then modeled as a function of children’s age (reported in years) and the between-subjects drawing condition in a non-linear generalized mixed-effect model. Consistent with prior work (Long, Fan, & Frank, 2018), we found a strong effect of age; older children produced overall more recognizable drawings (b = `r model_summary[1,'Estimate']`, SE =`r model_summary[1,'Std. Error']`, z = `r model_summary[1,'z value']`, p =`r model_summary[1,'Pr(>|z|)']`). Contrary to our expectations, we found that overall children did not draw more recognizable drawings in the perception or working memory conditions than the semantic condition (perception condition M =`r P_average`% recognized, semantic condition, M=`r S_average`%, working memory condition, M=`r W_average`%). However, we  found an interaction between age and the perception condition (b = `r model_summary[5,'Estimate']`, SE =`r model_summary[5,'Std. Error']`, z = `r model_summary[5,'z value']`, p =`r model_summary[5,'Pr(>|z|)']`):  younger children drew less recognizable drawings in the perception condition, while the recognizability of older children's drawings slightly increased.

We thus evidence in favor of a developmental difference in drawing from perception: while adults (Fan, Yamins, & Turk-Browne, 2018) produce more recognizable drawings when drawing from photographs, younger children showed the opposite trend, suggesting that the task of drawing from perception may have actually impaired their ability to draw recognizable images. Taken together, this work suggests younger children did not make use the visual information about what things look like to improve the recognizability of their drawings, hinting that a memory retrieval failure is not what explains the age-related changes in the recognizability of children’s drawings.  Future work will confirm this finding with a broader age range and set of items to explore aksdjfa;ksdfj;alsdkjfa;.


