---
title: "PhotoDraw-Analysis1"
author: "Bria Long"
date: "8/6/2018"
output: html_document
---

```{r setup, echo = FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
theme_set(theme_few())
```

## Load data and do basic preprocessing.
```{r}
## Read in data outputs from turk data - true/false recognition 
r <- read.csv("preprocessed_data/photodraw_recognition_ratings.csv") %>%
  as.tibble() 

## refactor levels to that semantic condition is first, then working memory, then perception
r$condition <- factor(r$condition, levels = c("S", "W", "P"))

d <- read_csv("preprocessed_data/photodraw_data_Aug8.csv") %>%
  select(-X1) %>%
  filter(!is.na(age)) %>%
  mutate(imNameShort = paste0(category, '_sketch', '_', session_id,'_',condition, '_', age,'.png'))

```

### Convert alphanumeric age to numeric age in python csv
```{r}
d <- d %>%
  group_by(session_id) %>%
  mutate(age_char = strsplit(age,"e")[[1]][2]) %>%
  mutate(age_num = as.numeric(age_char)) %>%
  select(-age) %>%
  rename(age = age_num)
```

## Join ratings and python datasets
```{r}
joined <- left_join(r,d)


```

### Look at num strokes / duration per condition
```{r}
##library("RColorBrewer")
##myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))

ggplot(d, aes(x = condition, y = num_strokes, col=age)) + 
    geom_jitter(width = .1, alpha = .5) 
  ##scale_colour_gradientn(colours = myPalette(100), limits=c(4, 7))

ggplot(d, aes(x = condition, y = draw_duration, col=age)) +
    geom_jitter(width = .1, alpha = .5) 

```

## How do num strokes / draw duration relate to recognizability?
```{r}
corByItem <- joined %>%
  group_by(imNameShort) %>%
  mutate(avgCorrect = mean(correct)) %>%
  distinct(imNameShort, avgCorrect, draw_duration, num_strokes, age, condition)

```

# Make some diagnostic plots...
```{r}
ggplot(corByItem, aes(x = num_strokes, y = avgCorrect, col=condition)) +
    geom_jitter(width = .1, alpha = .5) +
    facet_grid(~age)

ggplot(corByItem, aes(x = draw_duration, y = avgCorrect, col=condition)) +
    geom_jitter(width = .1, alpha = .5) +
    facet_grid(~age)
```


##look at average stroke length's distribution
```{r storke length}

corbyCategory <- joined %>%
  group_by(category)%>%
  multi_boot_standard(col = "avg_stroke_length")

cate <- left_join(joined,corbyCategory)

ggplot(cate,aes(x=category,y=mean))+
  geom_jitter(width = .1, alpha = .5)

ggplot(d,aes(x=category,y=avg_stroke_length,col=condition))+
  geom_jitter(width = .1, alpha = .5)


ggplot(d,aes(x=age,y=avg_stroke_length,col=condition))+
  geom_jitter(width = .1, alpha = .5)

```

## How do stroke length relate to recognizability?
```{r}
corByItem2 <- joined %>%
  group_by(imNameShort) %>%
  mutate(avgCorrect = mean(correct)) %>%
  distinct(imNameShort, avgCorrect, avg_stroke_length, age, condition)



ggplot(corByItem2, aes(x = avg_stroke_length, y = avgCorrect, col=condition)) +
    geom_jitter(width = .1, alpha = .5) +
    facet_grid(~age)


```


## relationship between average storke length and correctness
```{r}

corbyStrokeLength <- joined %>%
  group_by(avg_stroke_length,age)%>%
  multi_boot_standard(col = "correct")


ggplot(corbyStrokeLength,aes(x=avg_stroke_length,y=mean,col=age))+
  geom_jitter(width=.1)


```


## Sanity check number of raters per image
```{r}
ratersPerImage <- r %>%
  distinct(imageName, workerid) %>%
  group_by(imageName) %>%
  summarize(count = n()) 

assert_that(sum(ratersPerImage$count==30)==(length(unique(r$imageName))))

```

## Sanity check number of kids in each condition and age
```{r}
r %>%
  distinct(sessionId, condition, age) %>%
  group_by(condition) %>%
  summarize(count = n()) %>%
  kable()
```

## And distribution across age groups and conditions
```{r}
r %>%
  distinct(sessionId, condition, age) %>%
  group_by(condition,age) %>%
  summarize(count = n()) 
```

## Take a look at the raw rating data as a sanity check
Highest chosen category is correct one;  confusions look more or less reasonable.
```{r}
ratingConfusions <- r %>%
  group_by(category, rating)  %>%
  summarize(number = n()) %>%
  group_by(category) %>%
  mutate(prop = number / sum(number)) %>%
  complete(rating, fill = list(prop = 0))

ggplot(ratingConfusions, 
       aes(x = rating, y = category, fill = prop)) + 
  geom_tile() + 
  ylab("True Category") + 
  xlab("Rated as") + 
  scale_fill_gradient(limits = c(0, 1)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

## How different are individual participants?
```{r}

corbyChild <- r %>%
  group_by(sessionId) %>%
  multi_boot_standard(col = "correct")

indiv <- left_join(r,corbyChild) %>%
  mutate(sessionId = fct_reorder(sessionId, mean, .desc=TRUE))

ggplot(indiv, aes(x = sessionId, y = mean, col = age)) +
  geom_jitter(width = .1, alpha = .5) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```


##  How does recognizability vary across  condition only?
```{r}
## Get the percent recognized for each age group / condition
corbyConditionOnly <- r %>%
  group_by(condition) %>%
  multi_boot_standard(col = "correct")  

ggplot(corbyConditionOnly, aes(x = condition, y = mean, col=condition)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper))  

```



##  How does recognizability vary across age and condition, collapsing across items?
```{r}
## Get the percent recognized for each age group / condition
corbyCondition <- r %>%
  group_by(condition,age) %>%
  multi_boot_standard(col = "correct")  

ggplot(corbyCondition, aes(x = age, y = mean, col=age)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  facet_grid(~condition) 
```


```{r}
corbyChild <- r %>%
  group_by(condition,sessionId, age) %>%
  mutate(avgCorrect = mean(correct))

ggplot(corbyChild, aes(x = age, y = avgCorrect, col=age)) + 
  geom_jitter(width = .05, alpha = .5)  +
  facet_grid(~condition) 
  
```
## How does this trend break down by the catergory that children drew?
```{r}
corbyItem <- r %>%
  group_by(age,condition,category) %>%
  multi_boot_standard(col = "correct")  

ggplot(corbyItem, aes(x = condition, y = mean, col=age)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~category) 
```

```{r}
r$workerid = as.factor(r$workerid)
corbyWorked <- r %>%
  group_by(workerid) %>%
  mutate(avgCorrect = mean(correct)) %>%
  distinct(workerid, avgCorrect) %>%
  kable()
```

## Inferential analyses: Non-linear mixed effect model with random slopes for items and random intercepts for participants. 
```{r}
mod <- glmer(correct ~ age*condition + (1 | sessionId) + (1 | category),  data = r,  family = "binomial")
model_summary = round(summary(mod)$coef,3);
kable(model_summary, digits = 3)

```

## Exploratory analysis: We have a somewhat uneven distribution of kids across ages (though even across condition). Do these results hold when we bin by "younger" and "older" kids to get a more even split?
```{r}
r <- r %>%
  mutate(age_group = cut(age, c(3.9, 5, 8), labels = c("4-5","6-7"))) 
```

### Plot how accuracy differs by age group and condition
```{r}
corbyAgeGroup <- r %>%
  group_by(age_group, condition)%>%
  multi_boot_standard(col="correct")

ggplot(corbyAgeGroup, aes(x = condition, y = mean, col=age_group)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper))


```

### Run inferential model statistics for age group
```{r}
mod_age_group <- glmer(correct ~ age_group*condition + (1 | sessionId) + (1 | category),  data = r,  family = "binomial")
kable(summary(mod_age_group)$coef, digits = 3)
```

Looks like we still see an interaction between age_group and condition, though the main effect of 4-5 year-olds and 6-7 year-olds is no longer significant on it's own.


```{r}
mod <- glmer(correct ~ age*condition + (1 | sessionId) + (1 | category),  data = r,  family = "binomial")
model_summary = round(summary(mod)$coef,3);
kable(model_summary, digits = 3)

joined$condition = factor(joined$condition, levels = c(“S”, “W”, “P”))
mod <- glmer(correct ~ age*condition + (1 | sessionId) + (1 | category),  data = joined,  family = "binomial")
model_summary = round(summary(mod)$coef,3);
kable(model_summary, digits = 3)
```

### Grab out some values for easier rendering in abstract text.
```{r}
W_average = round(corbyConditionOnly$mean[corbyConditionOnly$condition=="W"],2)
P_average = round(corbyConditionOnly$mean[corbyConditionOnly$condition=="P"],2)
S_average = round(corbyConditionOnly$mean[corbyConditionOnly$condition=="S"],2)

num_children = length(unique(r$sessionId))

```

SRCD Abstract:

The role of memory in children’s drawings of object categories
Bria Long, Judy Fan, Yi Feng, Renata Chai, & Michael C. Frank

	Children’s drawings of object categories (e.g., rabbit, cat) become more and more recognizable as they get older, including visual features that distinguish these categories from one another (Long, Fan, & Frank, 2018). Why might older children tend to include these kinds of features (e.g., longer ears when drawing a rabbit)? One possibility is that younger children have a harder time accessing and retrieving their visual representations of what things tend to look like. Here, we examined whether children would draw more recognizable versions of objects when they heard a verbal cue accompanied by a picture of a canonical exemplar of this category (e.g., “can you draw a rabbit?”; working memory condition) and when they were asked to draw from perception (e.g., “can you draw this rabbit in the picture”) versus when they only heard a verbal cue (semantic condition).

	Children ages 4-7 years (N = `r num_children`  total; 20 children in each condition) participated in a quick drawing game designed to test this hypothesis and were randomly assigned to one of these three conditions and drew five object categories (cup, shoe, rabbit, cat, train). The recognizability of children’s drawings was then assessed via adult raters (N = 30 per image, N = 90 total) who completed a 22AFC task with identity of each object category; drawings were only counted as recognizable if the adult rater guessed the correct category. These recognition scores for each drawing were then modeled as a function of children’s age (reported in years) and the between-subjects drawing condition in a non-linear generalized mixed-effect model. Consistent with prior work (Long, Fan, & Frank, 2018), we found a strong effect of age; older children produced overall more recognizable drawings (b = XX, SE =XX, z = XX, p =XX). While overall children drew the least recognizable drawings in the perception condition (perception condition M = 29% recognized, semantic condition, M = 38% recognized, working memory condition, M = 40% recognized; main effect of condition, (b = XX, SE =XX, z = XX, p =XX), we also found an interaction between age and drawing condition (b = XX, SE =XX, z = XX, p =XX): older children drew more recognizable drawings in the perception condition, while younger children drew less recognizable drawings in the perception condition. In contrast, we found no such interaction for the working memory condition. 

We thus found a marked developmental difference in drawing from perception: while adults (Fan, Yamins, & Turk-Browne, 2018) produce more recognizable drawings when drawing from photographs, younger children showed the opposite trend, suggesting that the task of drawing from perception may have actually impaired their ability to draw recognizable images. Taken together, this work suggests younger children did not make use the visual information about what things look like to improve the recognizability of their drawings, hinting that a memory retrieval failure is not what explains the age-related changes in the recognizability of children’s drawings. 



Overall, we found that children in the perception condition actually drew the least recongizble drawings (perception condition M =`r P_average`% recognized, semantic condition, M=`r S_average`%, working memory condition, M=`r W_average`%).

