---
title: "AnimalGame-Recognition-Analyses"
author: "Bria Long"
date: "5/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(ggplot2)
library(assertthat)
library(langcog)
library(viridis)
library(ggthemes)
library(lme4)
```

## Import animalgame data &  Import classifications (4 way classification on 560 drawings)
```{r}
d <- read.csv("animalgame_v1_out_may8_final.csv") %>%
  as.tibble() 

c <- read.csv("compiled_classifications/classification-outputs-animalgame_C_0.1_560.csv") %>%
  as.tibble() %>%
  mutate(sketch_path = paste0(target_label,'_','sketch_age',age,'_cdm_',session_id)) %>%
  mutate(sketch_path = as.factor(sketch_path))
```

### Preprocess dataset
```{r}
# make similar levels
d$intended_category <- factor(d$intended_category, levels=levels(d$clicked_category))

# compute accurcy
d <- d %>%
  mutate(correct_or_not = (clicked_category == intended_category))  

d$recognizer_age <- factor(d$recognizer_age, levels = c('age2','age3','age4','age5','age6','age7','age8','age9','age10','adult'))
```

## Filter non-compliant subjects
```{r}
# get list of non-compliant subs
bad_subs <- d %>%
  group_by(sessionId) %>%
  filter(producer_age == "photo") %>%
  summarize(avg_photo_correct = mean(correct_or_not), count_trials = n()) %>%
  filter(avg_photo_correct < .5) 

# filter bad subs & weird trials
d <- d %>%
  filter(!sessionId %in% bad_subs$sessionId) %>%
  filter(RT>100 & RT<15000) 

count_subs_per_age <- d %>%
  group_by(recognizer_age) %>%
  summarize(num_subs = length(unique(sessionId)))

##
num_trials_per_kid <- d %>%
  group_by(sessionId) %>%
  mutate(max_trials = max(trial_num)) %>%
  distinct(sessionId,max_trials,recognizer_age) %>%
  group_by(sessionId) %>%
  summarize(average_trials = mean(max_trials))

```

We excluded `r length(bad_subs$sessionId)` subjects for having 'photo' accuracies of less than 50% correct; these subjects completed an average of `r mean(bad_subs$count_trials)` trials.

## Join classifications & recognition data
```{r}

## compute bins for distinctiveness
sketch_by_distinctiveness <- c %>%
  mutate(distinct_index = ntile(target_label_prob,10)) %>%
  select(sketch_path, distinct_index)

## filter recognition data to just kids and wrangle variables
kids_sketches_d <- d %>%
  filter(producer_age != 'photo') %>% # don't look at photo trials
  filter(recognizer_age != 'adult') %>%  # or adults
  ## wrangle sketch paths so can be joined with classification data
  mutate(sketch_path = as.factor(str_split_fixed(sketch_path,'/',2)[,2])) %>% 
  mutate(sketch_path = as.factor(str_split_fixed(sketch_path,'.png',2)[,1])) %>% 
  ## create numeric age & age bins
  mutate(recognizer_age_numeric = as.numeric(str_split_fixed(recognizer_age,'age',2)[,2])) %>%
  mutate(recognizer_age_group = cut(recognizer_age_numeric, c(1.9, 4, 6, 8, 10.1), labels = c("2-4 yrs","4-6 yrs","6-8 yrs","8-10 yrs"))) %>%
  mutate(recognizer_age_group_numeric = cut(recognizer_age_numeric, c(1.9, 4, 6, 8, 10.1), labels=c(2,4,6,8))) %>%
  mutate(recognizer_age_group_numeric = as.numeric(recognizer_age_group_numeric))

count_subs_per_age_bin <- kids_sketches_d %>%
  group_by(recognizer_age_group) %>%
  summarize(num_subs = length(unique(sessionId)))


## join distinctiveness bins for each sketch in dataset
all_joined <- kids_sketches_d %>%
  left_join(sketch_by_distinctiveness)
```


### Plot distinctivenss by age interaction
```{r}
distinct_by_age <- all_joined %>%
  group_by(recognizer_age_numeric, distinct_index) %>%
  multi_boot_standard(col='correct_or_not') %>%
  group_by(distinct_index)

ggplot(distinct_by_age, aes(x=distinct_index, y=mean, col=recognizer_age_numeric)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_smooth(alpha=.2, span=2) +
  facet_grid(~recognizer_age_numeric) +
  theme_few() + 
  scale_color_viridis(discrete=FALSE)
```

### Plot distinctivenss by age group interaction
```{r}
distinct_by_age <- v %>%
  group_by(recognizer_age_group, distinct_index) %>%
  multi_boot_standard(col='correct_or_not') %>%
  group_by(distinct_index)

(distinct_by_age_plot <- ggplot(distinct_by_age, aes(x=distinct_index, y=mean, col=recognizer_age_group)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_smooth(alpha=.2, span=2) +
  facet_grid(~recognizer_age_group) +
  theme_few(base_size = 22) + 
  scale_x_continuous(breaks=seq(1,10,2)) +
  xlab('Distinctiveness Index') +
  ylab('Proportion recognized') +
  theme(legend.position='none') + 
  scale_color_viridis(discrete=TRUE))

ggsave('DistinctByAge.pdf',distinct_by_age_plot, width=11)
```

### Explore how distinctivenss vs age group interact in glmer (won't converge with all recognizer ages...)
```{r}
model_lmer <- glmer(correct_or_not ~ distinct_index*recognizer_age_group_numeric + (1|intended_category) + (1|sessionId),  data = all_joined, family='binomial')
summary(model_lmer)
```


```{r}
joined_by_sketch <- all_joined %>%
  group_by(producer_age, distinct_index) %>%
  multi_boot_standard(col='correct_or_not') %>%
  group_by(distinct_index)

ggplot(joined_by_sketch, aes(x=producer_age, y=mean, col=distinct_index, group=distinct_index)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  theme_few()
```

```{r}
joined_by_sketch <- correct_sketch_by_distinctiveness %>%
  left_join(d_sum) %>%
  group_by(recognizer_age, high_vs_low_distinct) %>%
  multi_boot_standard(col='avg_correct') %>%
  group_by(high_vs_low_distinct)

ggplot(joined_by_sketch, aes(x=recognizer_age, y=mean, col=high_vs_low_distinct)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper))
```

```{r}
joined_by_sketch <- sketch_by_distinctiveness %>%
  left_join(d_sum) %>%
  group_by(recognizer_age, producer_age, high_vs_low_distinct) %>%
  multi_boot_standard(col='avg_correct') %>%
  group_by(high_vs_low_distinct)

joined_by_sketch$high_vs_low_distinct=as.factor(joined_by_sketch$high_vs_low_distinct)

ggplot(joined_by_sketch, aes(x=producer_age, y=mean, col=high_vs_low_distinct)) +
  geom_point(position = position_dodge(width=1)) +
  # geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha=.2) +
  theme_few() +
  geom_smooth() + 
  facet_grid(~recognizer_age) 

```

```{r}
joined_by_sketch <- correct_sketch_by_distinctiveness %>%
  left_join(d_sum) %>%
  filter(recognizer_age != 'adult') %>%
  mutate(recognizer_age_numeric = as.numeric(str_split_fixed(recognizer_age,'age',2)[,2])) %>%
  mutate(recognizer_age_group = cut(recognizer_age_numeric, c(1.9, 4, 6, 8, 10.1), labels = c("2-4 yrs","4-6 yrs","6-8 yrs","8-10 yrs"))) %>%
  group_by(recognizer_age_group, producer_age, high_vs_low_distinct) %>%
  multi_boot_standard(col='avg_correct')


levels(joined_by_sketch$producer_age) = c('4 yrs','5 yrs','6 yrs','7 yrs','8 yrs','photo')

ggplot(joined_by_sketch, aes(x=producer_age, y=mean, col=high_vs_low_distinct, group = high_vs_low_distinct)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.5)) +
  facet_grid(~recognizer_age_group) +
  theme_few(base_size=18) +
  ylab('Proportion recognized')+
  xlab('Age of drawer') +
  theme(legend.position='none')
  
  


```


```{r}
# dogs <- c %>%
#   filter(target_label=='dog') %>%
#   filter(correct_or_not == 0) %>%
#   rowwise() %>%
#   mutate(max_val = max(bird_prob, fish_prob, rabbit_prob)) %>%
#   mutate()
  

```

```{r}
cor_by_age <- c %>%
  group_by(age,target_label) %>%
  summarize(mean_cor = mean(target_label_prob))


ggplot(cor_by_age, aes(x=age, y=mean_cor, col=target_label)) +
  geom_jitter(height=.01, width=.2) 
```

```{r}
by_recognizer_distinct <- d %>%
  mutate(sketch_path = as.factor(str_split_fixed(sketch_path,'/',2)[,2])) %>%
  left_join(correct_sketch_by_distinctiveness)
  
```

## Compile averages to look at average correct
```{r plot-counts}
# summarize avg correct by producer age  
by_producer <- d %>%
  filter(recognizer_age!= 'adult') %>%
  group_by(producer_age) %>%
  multi_boot_standard(col = 'correct_or_not')

by_recognizer <- d %>%
  group_by(recognizer_age) %>%
  filter(producer_age != 'photo') %>%
  multi_boot_standard(col = 'correct_or_not')

by_recognizer_photo <- d %>%
  group_by(recognizer_age) %>%
  filter(producer_age == 'photo') %>%
  multi_boot_standard(col = 'correct_or_not') 






```

### Compile averages by RT
```{r}
# summarize avg correct by producer age  
by_producer_rt <- d %>%
  filter(recognizer_age!= 'adult') %>%
  group_by(producer_age) %>%
  filter(correct_or_not == TRUE) %>%
  filter(RT > 300 & RT < 20000) %>%
  multi_boot_standard(col = 'RT')

by_recognizer_rt <- d %>%
  group_by(recognizer_age) %>%
  filter(correct_or_not == TRUE) %>%
  filter(producer_age != 'photo') %>%
 filter(RT > 300 & RT < 20000) %>%
  multi_boot_standard(col = 'RT')

by_recognizer_photo_rt <- d %>%
  group_by(recognizer_age) %>%
  filter(producer_age == 'photo') %>%
  filter(correct_or_not == TRUE) %>%
  filter(RT > 300 & RT < 20000) %>%
  multi_boot_standard(col = 'RT') 

both_rt <- d %>%
  group_by(recognizer_age,producer_age) %>%
  filter(correct_or_not == TRUE) %>%
  filter(RT > 300 & RT < 10000) %>%
  multi_boot_standard(col = 'RT') 

```

```{r}

both_category <- d %>%
  group_by(producer_age,intended_category) %>%
  # filter(recognizer_age == "adult") %>%
  multi_boot_standard(col = 'correct_or_not') 

ggplot(both_category,aes(x=producer_age, y=mean, col=producer_age)) +
  theme_few() + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ylab('average correct') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), aspect.ratio = 1) +
  facet_grid(~intended_category) +
  scale_color_viridis(discrete=TRUE) 

### Plot at how each group is doing on the photo catch trials (this excludes 'bad' subs)

```

```{r}
by_recognizer$recognizer_age <- factor(by_recognizer$recognizer_age, levels = c('age2','age3','age4','age5','age6','age7','age8','age9','age10','adult'))

ggplot(by_recognizer,aes(x=recognizer_age, y=mean, col = recognizer_age)) +
  theme_few() +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  scale_color_viridis(discrete = "TRUE") + 
  ylab('Proportion drawings recognized') +
  ylim(.25,1) +
  geom_smooth() 
  
```

```{r}
by_recognizer_photo$recognizer_age <- factor(by_recognizer_photo$recognizer_age, levels = c('age2','age3','age4','age5','age6','age7','age8','age9','age10','adult'))

ggplot(by_recognizer_photo,aes(x=recognizer_age, y=mean, col = recognizer_age)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  scale_color_viridis(discrete = "TRUE") + 
  ylab('Proportion recognized - PHOTO')
```

### By producer age, collapsing across recognizer age
```{r}
ggplot(by_producer,aes(x=producer_age, y=mean, col = producer_age)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  scale_color_viridis(discrete = "TRUE") + 
  ylab('Proportion recognized')
```

## Now looking at producer x recognizer age
```{r}
both <- d %>%
  group_by(recognizer_age,producer_age) %>%
  multi_boot_standard(col = 'correct_or_not') 

levels(both$recognizer_age) = c('2 yrs','3 yrs','4 yrs','5 yrs','6 yrs','7 yrs','8 yrs','9 yrs','10 yrs','adult')
levels(both$producer_age) = c('4 yrs','5 yrs','6 yrs','7 yrs','8 yrs','photo')

(descriptives <- ggplot(both,aes(x=producer_age, y=mean, col=producer_age)) +
  theme_few(base_size=14) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ylab('Proportion recognized') +
  xlab('Age of drawer') + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1), aspect.ratio = 1, legend.position='none') +
  facet_wrap(~recognizer_age, scales='free_x') +
  scale_color_viridis(discrete=TRUE))

ggsave('mainResults.pdf', descriptives, width=6, height=8, dpi=300)
```

### Switch recognizer/producer age to re-visualize data
```{r}
both_plot <- both %>%
  group_by(recognizer_age)

ggplot(both_plot,aes(x=recognizer_age, y=mean, col=producer_age)) +
  theme_few() + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ylab('average correct') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), aspect.ratio = 1) +
  facet_grid(~producer_age) +
  scale_color_viridis(discrete=TRUE) +
  geom_smooth()

```

### Check out RTs
```{r}
both_rt$recognizer_age <- factor(both_rt$recognizer_age, levels = c('age2','age3','age4','age5','age6','age7','age8','age9','age10','adult'))

ggplot(both_rt,aes(x=producer_age, y=mean, col=recognizer_age)) +
  # geom_point() + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab('average RT') + 
  facet_grid(~recognizer_age) 
```


```{r}
# library(lme4)
#  model_lmer <- glmer(correct_or_not ~ producer_age*recognizer_age + (1 | intended_category),  data = d, family="binomial", optimizer="bobqa")


```