---
title: "Render valid/invalid drawings post filtering"
author: ""
date: "9/3/2020"
output: html_document
---

```{r}
library(tidyverse)
library(assertthat)
```

## Set paths and output directories
```{r}
# create output paths
which_run = 'cdm_run_v7' # change -- v4, v5, v6, v7 are possible options
drawing_path = here::here('data/drawings',which_run)
filtered_dataset_path =  fs::path(drawing_path,'filtered_dataset')
filtered_dataset_descriptives_path =  fs::path(drawing_path,'filtered_dataset_descriptives')
filtered_dataset_descriptives_file = fs::dir_ls(filtered_dataset_descriptives_path)[2] # second file in this directory
print(filtered_dataset_descriptives_file)

cleaned_full_dataset_path = here::here('data/drawings','stringent_cleaned_dataset')
cleaned_full_meta_path = here::here('data/drawings', 'stringent_cleaned_dataset_meta')
```
## make dirs for rendering bad drawings
```{r}
called_invalid_twice = fs::path(drawing_path, 'called_invalid_twice')
called_invalid_once = fs::path(drawing_path, 'called_invalid_once')
dir.create(called_invalid_twice)
dir.create(called_invalid_once)

```


## Load csvs from python outputs of db_records and filtering records
```{r}
# db records -- logs if/who has seen a particular image during a filtering task
db_records <-read_csv(paste0('filtering_outputs/','images_checked_', which_run,'.csv')) %>%
  select(filename, games, numGames)

# filtering logs -- has one record for each drawing that was marked invalid
joined_filtering = read_csv(paste0('filtering_outputs/','marked_invalid_drawings_',which_run,'.csv')) %>%
  as_tibble() %>%
  rename(filename = '0', worker_id = 'X1') %>%
  group_by(filename) %>%
  dplyr::summarize(count_invalid = length(unique(worker_id))) %>%
  left_join(db_records) 

```


## Create dfs for images that were marked invalid once or more than once
```{r}
filtered_once <- joined_filtering %>%
  filter(numGames>1) %>%
  filter(count_invalid==1)

filtered_twice<- joined_filtering %>%
  filter(numGames>1) %>%
  filter(count_invalid>1)

filtered_at_all<- joined_filtering %>%
  filter(numGames>1) %>%
  filter(count_invalid>0)

valid_images <- db_records %>%
  filter(!filename %in% filtered_at_all$filename) %>%
  distinct(filename)

```
For `r which_run`, we had prolific workers filter `r length(db_records$filename)`, and `r length(filtered_at_all$filename)` were marker invalid.


## Save out metadata for each run
```{r}
meta <- read_csv(filtered_dataset_descriptives_file) %>%
  select(-filename, -fileNameShort, -X1) %>%
  rename(filename = fileNameShortNew) 

meta_valid_images <- meta %>%
  right_join(valid_images, by=c('filename')) %>%
  distinct(filename, session_id, category, age, age_numeric, num_strokes, draw_duration_new, draw_duration_old, mean_intensity)

assert_that(length(meta_valid_images$filename) == length(valid_images$filename))
what <- meta_valid_images %>%
  filter(!filename %in% valid_images$filename)

write_csv(meta_valid_images, path = fs::path(cleaned_full_meta_path, paste0(which_run,'_cleaned.csv')))
```


## Save images out to those directories; commented since already done
```{r eval=FALSE}
# file.copy(from = file.path(filtered_dataset_path, filtered_twice$filename), to = file.path(fs::path(called_invalid_twice, filtered_twice$filename)))
# 
# file.copy(from = file.path(filtered_dataset_path, filtered_once$filename), to = file.path(fs::path(called_invalid_once, filtered_once$filename)))

# file.copy(from = file.path(filtered_dataset_path, valid_images$filename), to = file.path(fs::path(cleaned_full_dataset_path, valid_images$filename)))
```

# only do once -- copying cogsci drawings to new directory for better organization
```{r}
# only do once -- copying cogsci drawings
# which_run = 'cogsci_2019_filtered'
# filtered_dataset_path = here::here('data/drawings',which_run)
# cleaned_full_dataset_path = here::here('data/drawings','stringent_cleaned_dataset')
# 
# file.copy(from = fs::path(filtered_dataset_path,dir(filtered_dataset_path)), to = file.path(fs::path(cleaned_full_dataset_path)))
```